### 2015-10-02 test.tex
First commit

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\begin{document}
\title{System Architecture for a Class of Small Service Vehicle}
\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
	Homer Simpson\IEEEauthorrefmark{2},
	James Kirk\IEEEauthorrefmark{3}, 
	Montgomery Scott\IEEEauthorrefmark{3} and
		Eldon Tyrell\IEEEauthorrefmark{4}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
	Georgia Institute of Technology,
Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
	Email: homer@thesimpsons.com}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
	Telephone: (800) 555--1212, Fax: (888) 555--1212}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
\maketitle

\begin{abstract}
By the dawn of the new millennium, robotics has undergone a major transformation scope and dimensions. This expansion has been brought about by the maturity of field and the advances in its related technologies. From a largely dominant focus, robotics has been rapidly expanding into the challenges of the world. The recent technology development demonstrated how the fast growing progress toward the of new perception, control, and motion planning techniques allow autonomous vehicles not only to travel significant distances in off-road, but also to operate in urban scenarios. The expected impact in the commercial sector for automotive manufacturers is equally if not more: autonomous sensing and control constitute key technologies to vehicles the future that might help save thousands of lives now lost in traffic accidents.

Imagine a large field of vehicles without drivers traversing 60 miles in live, operating entirely without human guidance. A complex course including, traffic circles, and parking lots, defined by just kilobytes of data, several meters wide traveling down lanes only slightly wider, using systems with an accuracy of several meters. Humans in full-size unmanned vehicles at speeds up to 60 miles per hour. This actually would become reality in the near future.

This project aims to bring the recent development on autonomous driving technology into a more practical and marketable platform so that it benefits can really be advantageous to real users \cite{mrx05,IEEEexample:bluebookstandard,IEEEexample:softonline,Dellaert06ijrr}.
\end{abstract}
%,./IEEEtranBST/IEEEexample.bib

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,./IEEEtranBST/IEEEexample,isam}
\end{document}

### 2015-10-16 sample-paper/sample-paper_IEEE_cited_biblatex_biber.tex
now can cite using pandoc for IEEEtran .bst format

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\usepackage[usenames,dvipsnames]{color}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Donald Duck},
            pdftitle={A sample paper},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{biblatex}
\addbibresource{sample-library.bib}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

\title{A sample paper}
\author{Donald Duck}
\date{October 1, 2014}

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\begin{document}
\maketitle
\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua. Ut enimad minim
veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
occaecat cupidatat non proident, sunt in culpa qui officia deserunt
mollit anim id est laborum.
\end{abstract}

\section{Section 1}\label{section-1}

\subsection{Subsection 1.1}\label{subsection-1.1}

Lorem \emph{ipsum} \textbf{dolor} sit amet, consectetur adipisicing
elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi
ut aliquip ex ea commodo consequat.

\subsection{Subsection 1.2}\label{subsection-1.2}

Sed ut perspiciatis unde omnis iste natus error sit voluptatem
accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab
illo inventore veritatis et quasi architecto beatae vitae dicta sunt
explicabo.

\begin{itemize}
\tightlist
\item
  one item
\item
  two items
\item
  three items
\item
  four items
\end{itemize}

Sed ut perspiciatis unde omnis iste natus error sit voluptatem
accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab
illo inventore veritatis et quasi architecto beatae vitae dicta sunt
explicabo.

You can enter LaTeX equations as inline math: such as
\(({e}^{i\pi }+1=0)\) or:

\(\mathbf{V}_1 \times \mathbf{V}_2 = \begin{vmatrix} \mathbf{i} & \mathbf{j} & \mathbf{k} \\ \frac{\partial X}{\partial u} & \frac{\partial Y}{\partial u} & 0 \\ \frac{\partial X}{\partial v} & \frac{\partial Y}{\partial v} & 0 \end{vmatrix}\)

\section{Section 2}\label{section-2}

\subsection{Subsection 2.1}\label{subsection-2.1}

Sed ut perspiciatis unde omnis iste natus error sit voluptatem
accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab
illo inventore veritatis et quasi architecto beatae vitae dicta sunt
explicabo.

Sed ut perspiciatis unde omnis iste natus error sit voluptatem
accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab
illo inventore veritatis et quasi architecto beatae vitae dicta sunt
explicabo \href{http://www.http://daringfireball.net}{link}. You enter
citations using @ and bibtex citation key, such as
\textcite{donaldduck2014} if you want only the year in brackets, or
\autocite{donaldduck2013} for a normal ciation in author-date form
within brackets.

This is the code for an image. Much simpler than in LaTeX. But you can
also use LaTeX code here. Just keep in mind that LaTeX code is only
rendered when converted to PDF. Conversion to Word or html won't pick it
up.

%\begin{figure}[htbp]
%\centering
%\includegraphics{sample-image.jpg}
%\caption{image caption}
%\end{figure}

\section{References}\label{references}

The reference list is added here automatically by Pandoc:

\printbibliography

\end{document}

### 2015-10-16 sample-paper/sample-paper_IEEE_cited_bibtex.tex
now can cite using pandoc for IEEEtran .bst format

--- 2015-10-16 sample-paper/sample-paper_IEEE_cited_biblatex_biber.tex
@@
-\documentclass[]{article}
+\documentclass[a4paper,12pt]{article}
+\usepackage{geometry}
+\geometry{left=3cm,right=3cm,top=3cm,bottom=3cm,footskip=2cm}
+\usepackage{setspace}	
+\linespread{1.3}
+
 \usepackage{lmodern}
@@
 }{}
+%\usepackage{biblatex}
+%\bibliography{sample-library.bib}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 \ifxetex
@@
 \fi
-\usepackage[usenames,dvipsnames]{color}
 \hypersetup{breaklinks=true,
@@
 \urlstyle{same}  % don't use monospace font for urls
-\usepackage{biblatex}
-\addbibresource{sample-library.bib}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 \setlength{\parindent}{0pt}
@@
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 \setcounter{secnumdepth}{0}
@@
 \date{October 1, 2014}
-
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
 
@@
 \begin{itemize}
-\tightlist
+%\tightlist
 \item
@@
 citations using @ and bibtex citation key, such as
-\textcite{donaldduck2014} if you want only the year in brackets, or
-\autocite{donaldduck2013} for a normal ciation in author-date form
+\cite{donaldduck2014} if you want only the year in brackets, or
+\cite{donaldduck2013} for a normal ciation in author-date form
 within brackets.
@@
 
-%\begin{figure}[htbp]
-%\centering
-%\includegraphics{sample-image.jpg}
-%\caption{image caption}
-%\end{figure}
+\begin{figure}[htbp]
+\centering
+\includegraphics{sample-image.jpg}
+\caption{image caption}
+\end{figure}
 
@@
 
-\printbibliography
+%\printbibliography
+
+\bibliographystyle{IEEEtran}
+\bibliography{sample-library}
 

### 2015-10-16 sample-paper/sample-paper.tex
a simple trix exampling referencing in latex, with latex command direct in pandoc markdown

--- 2015-10-16 sample-paper/sample-paper_IEEE_cited_bibtex.tex
@@
 }{}
-%\usepackage{biblatex}
-%\bibliography{sample-library.bib}
 \usepackage{graphicx}
@@
 explicabo \href{http://www.http://daringfireball.net}{link}. You enter
-citations using @ and bibtex citation key, such as
-\cite{donaldduck2014} if you want only the year in brackets, or
-\cite{donaldduck2013} for a normal ciation in author-date form
-within brackets.
+citations using @ and bibtex citation key, such as Duck (2014) if you
+want only the year in brackets, or (Duck 2013) for a normal ciation in
+author-date form within brackets.
 
@@
 rendered when converted to PDF. Conversion to Word or html won't pick it
-up.
+up. And see that figure referenced see \ref{fig:mylabel}.
 
@@
 \includegraphics{sample-image.jpg}
-\caption{image caption}
+\caption{image \label{fig:mylabel} caption}
 \end{figure}
@@
 
-%\printbibliography
+\hyperdef{}{ref-donaldduck2013}{\label{ref-donaldduck2013}}
+Duck, Donald. 2013. ``Turning Nothing into Money.'' \emph{Money
+Transactions} 15: 205--246.
 
-\bibliographystyle{IEEEtran}
-\bibliography{sample-library}
+\hyperdef{}{ref-donaldduck2014}{\label{ref-donaldduck2014}}
+---------. 2014. ``Turning Something Else into Money.'' \emph{Money
+Money Journal} 5: 101--141.
 

### 2015-10-17 fig_ex.py
added figure from .png and .pdf file

@@ -1,0 +1,24 @@
+# -*- coding: utf-8 -*-
+
+import matplotlib as mpl
+# mpl.use("pgf")
+pgf_with_pdflatex = {
+    "pgf.texsystem": "pdflatex",
+    "pgf.preamble": [
+         r"\usepackage[utf8x]{inputenc}",
+         r"\usepackage[T1]{fontenc}",
+         r"\usepackage{cmbright}",
+         ]
+}
+mpl.rcParams.update(pgf_with_pdflatex)
+
+import matplotlib.pyplot as plt
+plt.figure(figsize=(4.5,2.5))
+plt.plot(range(5))
+plt.text(0.5, 3., "serif", family="serif")
+plt.text(0.5, 2., "monospace", family="monospace")
+plt.text(2.5, 2., "sans-serif", family="sans-serif")
+plt.xlabel(u"µ is not $\\mu$")
+plt.tight_layout(.5)
+# plt.savefig('fig_ex.pdf')
+plt.savefig('fig_ex.png')

### 2015-10-21 fig_ex.py
matplotlib can use Agg backend to output eps

@@ -2,6 +2,7 @@
 
 import matplotlib as mpl
 # mpl.use("pgf")
+mpl.use("Agg")
 pgf_with_pdflatex = {
     "pgf.texsystem": "pdflatex",
     "pgf.preamble": [
@@ -21,4 +22,5 @@ plt.text(2.5, 2., "sans-serif", family="sans-serif")
 plt.xlabel(u"µ is not $\\mu$")
 plt.tight_layout(.5)
 # plt.savefig('fig_ex.pdf')
-plt.savefig('fig_ex.png')
+# plt.savefig('fig_ex.png')
+plt.savefig('fig_ex.eps')

### 2015-10-21 ieee-pandoc-template/paper.tex
finished first draft template

\documentclass[conference]{IEEEtran}
%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
%\documentclass[conference]{IEEEconf}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript

\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}

\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={System Architecture for a Class of Small Service Vehicle},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[numbers,square]{natbib}
\bibliographystyle{IEEEtranN-nourl}

\usepackage{listings}

\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\graphicspath{ {./figures/} }

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\title{System Architecture for a Class of Small Service Vehicle}

\author{
            \IEEEauthorblockN{Saputra, V. B.}
        \IEEEauthorblockA{%
            Institute for Infocomm Research \\
            Singapore \\
            saputravb@i2r.a-star.edu.sg}
         \and
            \IEEEauthorblockN{Ravichandiran, B.}
        \IEEEauthorblockA{%
            Institute for Infocomm Research \\
            Singapore \\
            ravib@i2r.a-star.edu.sg}
        }

\date{}

\usepackage{color}

\definecolor{lightred}{RGB}{175,50,50}
\definecolor{lightgreen}{RGB}{0,150,0}
\definecolor{lightblue}{RGB}{50,50,175}

\lstdefinelanguage{diff}{
  morecomment=[f][\color{lightblue}]{diff },
  morecomment=[f][\color{lightblue}]{index },
  morecomment=[f][\color{lightblue}]{@@},     % group identifier
  morecomment=[f][\color{lightred}]-,         % deleted lines
  morecomment=[f][\color{lightgreen}]+,       % added lines
  morecomment=[f][\color{lightblue}]{---}, % Diff header lines (must appear after +,-)
  morecomment=[f][\color{lightblue}]{+++},
}
\hyphenation{}

\newcommand{\attn}[1]{{\color{red}#1}}
\newcommand{\desc}[1]{{\emph{\color{blue}#1}}}
\newcommand{\needcite}{\attn{\tiny{[cite]}}}
\newcommand{\todo}[1]{\colorbox{yellow}{\bf TODO: #1}}

\lstset{ %
  basicstyle=\ttfamily\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  columns=fixed,
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=10pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny, % the style that is used for the line-numbers
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  tabsize=2,                       % sets default tabsize to 2 spaces
}

\urlstyle{rm}

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\begin{document}
\maketitle

\begin{abstract}
By the dawn of the new millennium, robotics has undergone a major
transformation scope and dimensions. This expansion has been brought
about by the maturity of field and the advances in its related
technologies. From a largely dominant focus, robotics has been rapidly
expanding into the challenges of the world. The recent technology
development demonstrated how the fast growing progress toward the of new
perception, control, and motion planning techniques allow autonomous
vehicles not only to travel significant distances in off-road, but also
to operate in urban scenarios. The expected impact in the commercial
sector for automotive manufacturers is equally if not more: autonomous
sensing and control constitute key technologies to vehicles the future
that might help save thousands of lives now lost in traffic accidents.
Imagine a large field of vehicles without drivers traversing 60 miles in
live, operating entirely without human guidance. A complex course
including, traffic circles, and parking lots, defined by just kilobytes
of data, several meters wide traveling down lanes only slightly wider,
using systems with an accuracy of several meters. Humans in full-size
unmanned vehicles at speeds up to 60 miles per hour. This actually would
become reality in the near future. This project aims to bring the recent
development on autonomous driving technology into a more practical and
marketable platform so that it benefits can really be advantageous to
real users.
\end{abstract}

\begin{IEEEkeywords}
    automobiles;
    feature extraction;
    intelligent transportation systems;
    mobile robots;
    optical scanners;
    path planning;
    trajectory control;
    autonomous service vehicle;
    drive-by-wire system;
    driverless car;
    electronic car;
    lane detection algorithm;
    lane keeping assistant;
    laser scanner;
    map free lane following;
    path planning;
    vehicle trajectory;
    Laser radar;
    Mobile robots;
    Path planning;
    Roads;
    Testing;
    Vehicles;
    Wheels\end{IEEEkeywords}

\thanks{*This work was supported by Autonomous Vehicle Department, Institute for Infocomm Research}

\section{Introduction}\label{introduction}

The computational requirements for autonomous driving are very
demanding, because autonomous vehicles have to process large amount of
online and offline data in order to sense and understand their
environment within long range safety distances with high precision, make
and perform driving decisions at real-time. Most current autonomous
vehicle prototypes around the world employ powerful distributed systems
consisting of multiple heterogeneous processors and systems for sensory
data processing, sensor fusion, intelligent behavior, and driving
control. These types of prototype systems are bulky, costly and power
hungry, thus are not suitable for real world deployment. Recently, Audi
developed an all-in-one embedded platform code named zFAS which
incorporates multiple heterogeneous processors (ECU/MCUs, Application
Processors, GPUs, FPGA and a video detection subsystem) on a single
tightly integrated board with specialized communication architecture
(including Deterministic Ethernet) to suit autonomous driving needs. The
computing power equals to the entire electronics architecture of today's
Audi vehicles, yet at a fraction of the size, cost and power
consumption. Such a platform is invaluable to eventually bring
autonomous driving technologies to the mass market.

This paper aims to describe and propose a generic design of the system
architecture based on the chosen compute components and the
characteristics / requirements of sensor fusion and autonomous driving
applications, integration, test and characterization for a class of
small service vehicle.

\section{Architecture}\label{architecture}

Components of a typical autonomous or assistive driving system could be
summarized in Fig. \ref{fig_1}. The system heavily depends on various
types of sensory data and sensors of the same type are synced with one
another through data sync modules. To make sense of sensor data, raw
data processing is required for different types of available data.
Overlapping field of views from different sensors could be combined and
the processing result is fused through a Low Level Fusion module. This
module also does some filtering to eliminate local noises and thus, make
the information more robust to small disturbances. The output objects
and localization data from low level fusion modules are then sent to a
High Level Fusion Module whereby all objects and filtered sensor
information are fused together to form a world model.

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{HighLevel.pdf}
\caption{Block Diagram of an autonomous vehicle driving system.}
\label{fig_1}
\end{figure}

\subsection{Middleware}\label{middleware}

{[}XME? Please fill in{]}

\section{Components}\label{components}

\subsection{Drive-By-Wire}\label{drive-by-wire}

\subsection{Control}\label{control}

Fig \ref{fig_2} shows a control error during simulation. A Stanley
controller can be used for different type of course, such as parking,
low speed, and medium travels.

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{fig_ex.pdf}
\caption{Example of matplotlib graph (vector graphic in the paper).}
\label{fig_2}
\end{figure}

\subsection{Path Planning}\label{path-planning}

Path planning done by \citeauthor{SongZW_IV_2015} has revealed the fact
that small service vehicle can be robustly navigate the path as long as
the localization gives its correct position. For more examples, readers
are encouraged to read \citep{Corley-etal_2011}. In addition,
\citet{Corley-etal_2012} confirmed that localization can be affected by
surrounding dynamic environment changes such as parked cars, and moving
pedestrians. \citet{Aalst-etal_2004} proposed a solution to this, but
later the work has been verified not working in
\citep{Abadi-etal_2008, Abebe-etal_2009}. For more references on this
problem, suggested readings are
\citep{Ackerman-Halverson_1998, Agrawal-etal_1998, Ali-etal_2012, Alipour-etal_2013}.

\subsection{Mapping}\label{mapping}

Procedure of mapping includes:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Point cloud assembly
\item
  Point cloud registration
\item
  Extracting useful information
\end{enumerate}

\subsubsection{Point cloud assembly}\label{point-cloud-assembly}

The assembly process is aggregating several point cloud frames from
sensor scans with some process of point cloud matching and registration.

\subsubsection{Point cloud registration}\label{point-cloud-registration}

\subsubsection{Extracting useful
information}\label{extracting-useful-information}

\begin{itemize}
\tightlist
\item
  Road curb
\item
  Traffic signs/lights
\item
  Building features
\end{itemize}

\paragraph{Road curb}\label{road-curb}
Road curb is the most reliable feature in road boundary detection. It is
easy to detect and currently it is the baseline for localization.

\paragraph{Traffic signs/lights}\label{traffic-signslights}

\paragraph{Building features}\label{building-features}

\subsection{Localization}\label{localization}

The localization is done by modeling the problem using \emph{Gamma
function} satisfying \(\Gamma(n) = (n-1)!\quad\forall n\in\mathbb N\) is
via the \textbf{euler} integral:

\begin{equation}
\label{eqn_example1}
x = \sum\limits_{i=0}^{z} 2^{i}Q
\end{equation}

\begin{equation}
\label{eqn_example2}
\Gamma(z) = \int_0^\infty t^{z-1}e^{-t}dt\,.
\end{equation}

\begin{equation}
\label{eqn_example3}
\mathbf{V}_1 \times \mathbf{V}_2 =  \begin{vmatrix}
\mathbf{i} & \mathbf{j} & \mathbf{k} \\
\frac{\partial X}{\partial u} &  \frac{\partial Y}{\partial u} & 0 \\
\frac{\partial X}{\partial v} & \frac{\partial Y}{\partial v} & 0
\end{vmatrix}
\end{equation}

Equation (\ref{eqn_example2}) is convoluted by means of \emph{Gaussian
Distribution}. In other words, (\ref{eqn_example1}) depicts the spectrum
of (\ref{eqn_example2}). The \textbf{eigen }matrix for the point cloud
distribution is given in (\ref{eqn_example2}).

\section{Safety Consideration}\label{safety-consideration}

Safety is very important in a critical mission project like autonomous
service vehicle. Not only that robust operation is required, but also
human safety must be prioritized in the system logic. Some components in
the system that needs attention are listed in Table \ref{table_example}.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{A Simple Example Table, IEEE standard format}
\label{table_example}
\centering
\begin{tabular}{c||c}
\hline\bfseries Component & \bfseries Risk\\
\hline
\hline Drive-By-Wire & Malfunction of motors\\
\hline
\hline GPS & GPS denied\\
\hline
\hline Camera & Cable loose\\
\hline
\end{tabular}
\end{table}

\section{Experimentation}\label{experimentation}

Fig. \ref{coms1_bare} shows the first vehicle platform that we first
retrofitted for the autonomous vehicle project.

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{coms1_bare}
\caption{Experimentation of building vehicle platform.}
\label{coms1_bare}
\end{figure}

\subsection{Sensors}\label{sensors}

Placement of the sensors on the autonomous vehicle can be seen in Fig.
\ref{ipe_ex}, and their connection to the system can be summarized in
Fig. \ref{dia_ex}.

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{ipe_ex.pdf}
\caption{Placement of sensors.}
\label{ipe_ex}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{dia_ex.pdf}
\caption{Diagram of sensors connection.}
\label{dia_ex}
\end{figure}

\section{Conclusion}\label{conclusion}

That's all folks!

\section*{Acknowledgments}\label{acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}

Thanks the AV team in I2R that can accomplish many wonderful demos
within very short period of time. This leads to the conception of this
paper and many outstanding results that have been used in the demos.

                                    \renewcommand\refname{References}
                        \bibliography{papers}

\end{document}

### 2015-10-21 ieee-pandoc-template/paper.tex
conformed with the conference format; WARNING: use the .cls from latest distro

@@
-\documentclass[conference]{IEEEtran}
-%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
-%\documentclass[conference]{IEEEconf}
+%\documentclass[10 pt,letterpaper,conference]{IEEEtran}
+%\documentclass[10 pt,letterpaper,conference]{IEEEconf}
+\documentclass[10 pt,letterpaper,conference]{IEEEtran}
 
@@
 
-\setlength{\parindent}{0pt}
+%\setlength{\parindent}{0pt}
 \setlength{\parskip}{6pt plus 2pt minus 1pt}
@@
 		Institute for Infocomm Research \\
-            Singapore \\
+		1 Fusionopolis Way, Singapore 138632 \\
 	saputravb@i2r.a-star.edu.sg}
@@
 		Institute for Infocomm Research \\
-            Singapore \\
+		1 Fusionopolis Way, Singapore 138632 \\
 	ravib@i2r.a-star.edu.sg}
@@
 % Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+%\ifx\paragraph\undefined\else
+%\let\oldparagraph\paragraph
+%\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+%\fi
+%\ifx\subparagraph\undefined\else
+%\let\oldsubparagraph\subparagraph
+%\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+%\fi
 
@@
 
-\begin{IEEEkeywords}
-    automobiles;
-    feature extraction;
-    intelligent transportation systems;
-    mobile robots;
-    optical scanners;
-    path planning;
-    trajectory control;
-    autonomous service vehicle;
-    drive-by-wire system;
-    driverless car;
-    electronic car;
-    lane detection algorithm;
-    lane keeping assistant;
-    laser scanner;
-    map free lane following;
-    path planning;
-    vehicle trajectory;
-    Laser radar;
-    Mobile robots;
-    Path planning;
-    Roads;
-    Testing;
-    Vehicles;
-    Wheels\end{IEEEkeywords}
+%%\begin{IEEEkeywords}
+%    %automobiles;
+%    %feature extraction;
+%    %intelligent transportation systems;
+%    %mobile robots;
+%    %optical scanners;
+%    %path planning;
+%    %trajectory control;
+%    %autonomous service vehicle;
+%    %drive-by-wire system;
+%    %driverless car;
+%    %electronic car;
+%    %lane detection algorithm;
+%    %lane keeping assistant;
+%    %laser scanner;
+%    %map free lane following;
+%    %path planning;
+%    %vehicle trajectory;
+%    %Laser radar;
+%    %Mobile robots;
+%    %Path planning;
+%    %Roads;
+%    %Testing;
+%    %Vehicles;
+%    %Wheels%\end{IEEEkeywords}
+%
 
@@
 \paragraph{Road curb}\label{road-curb}
+
 Road curb is the most reliable feature in road boundary detection. It is

### 2015-12-15 ieee-pandoc-template/paper.tex
continue writing towards IVS2015

@@
 
-{[}XME? Please fill in{]}
+Middleware refers to the software component that connects the various
+modules across network distributed system. It makes communication
+transparent to connected modules by providing reliability, consistency,
+security, and privacy capabilities. In our architecture
+CHROMOSOME\citep{CHROMOSOME} a Message-oriented middleware is used.
+CHROMOSOME implements publish-subscribe message paradigm, which also
+provides more guarantees with respect to the behaviour of distributed
+applications. \citep{buckl2014chromosome} The other alternative
+middlewares are Robotics Operating System (ROS) \citep{quigley2009ros}
+and OpenRTM-aist \citep{ando2005rt} which are commonly used in the field
+of Robotics.
 
@@
 
-\section{Safety Consideration}\label{safety-consideration}
+..Or, using numbering and some examples of referencing them given above.
+
+\subsection{Path Planning}\label{path-planning-1}
+
+Citations examples\ldots{}
+
+Path planning done by \citeauthor{SongZW_IV_2015} has revealed the fact
+that small service vehicle can be robustly navigate the path as long as
+the localization gives its correct position. For more examples, readers
+are encouraged to read \citep{Corley-etal_2011}. In addition,
+\citet{Corley-etal_2012} confirmed that localization can be affected by
+surrounding dynamic environment changes such as parked cars, and moving
+pedestrians. \citet{Aalst-etal_2004} proposed a solution to this, but
+later the work has been verified not working in
+\citep{Abadi-etal_2008, Abebe-etal_2009}. For more references on this
+problem, suggested readings are
+\citep{Ackerman-Halverson_1998, Agrawal-etal_1998, Ali-etal_2012, Alipour-etal_2013}.
+
+\subsection{Control}\label{control-1}
+
+Vehicle control or autonomous navigation is one of the key component for
+autonomous vehicle. Vehicle control performs necessary action to follow
+the intended path generated by path planner for smoother navigation
+towards destination point. The gas, brake control for longitudinal
+direction will be handled by velocity control and the steering control
+for turning across lateral direction will handled by lateral control
+module.
+
+\subsubsection{Velocity control}\label{velocity-control}
+
+Velocity control will estimate the gas, brake motor position in the
+drive by wire system for maintaining the desired velocity and braking
+for the vehicle. The desired velocity of the vehicle is determined with
+the modules input such as path planning, obstacle detection and health
+monitoring system. For autonomous lateral control the fixed constant
+velocity will not be a wise choice, since the navigation path is not
+always straight line of travel. The path may consists of various turns
+and unexpected circumstances like obstacles. For smoother path following
+and avoid jerkiness of vehicle, speed profiling have to done based on
+path curvatures and speed limits. Based on the data collected by manual
+driving, the speed is calculated for various path curvatures (turns).
+During the local path generation, the curvature of path is calculated
+and desired speed will be assigned to each curvatures across the path.
+To avoid rapid speed change and to make velocity transition smooth from
+straight line to curvature areas velocity averaging is performed in the
+direction of end to path start. Apart from speed determined by speed
+profiler across the path, in event of obstacle detection vehicle will
+also perform action like slow down or stops based on obstacle detected
+distance. In the event of certain module error or network communication
+failure, health monitoring system will perform stop action based on
+severity of error. To achieve desired velocity, the controller need to
+calculate the desired gas/brake position of the motor. Thus one of the
+frequently used controller technique closed loop PID controller is
+implemented. The closed loop PID controller helps in noise rejection and
+robustness of control with design flexibility. Based on desired
+velocity, the controller will calculate the motor position and passes to
+drive by wire (DBW) system. Drive by wire system will convert controller
+command to control signal and passes to the motor. The wheel encoder
+will help to measure the speed precisely and feedback to the controller
+for the necessary action. The block diagram of the velocity control
+implementation is shown in Fig \ref{fig_vel_control}.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.5in]{pid_velocity.pdf}
+\caption{Velocity control based on closed loop PID.}
+\label{fig_vel_control}
+\end{figure}
+
+\subsubsection{Lateral Control}\label{lateral-control}
+
+Lateral control aims to control the steering angle of the vehicle based
+on trajectory generated by path planner. In our study we have developed
+lateral controller based on Stanley's \citep{ventures2006stanley}
+steering controller. Stanley steering controller is one of the popular
+geometric path tracking approach used by Stanford university's
+autonomous vehicle during DARPA grand challenge 2006. he closed-loop
+geometric tracking controller helps vehicle to follow the desired path
+generated by path planning. The controller is based on non-linear cross
+track error \(C_{e}\) and heading error \(\theta_{e}\). Cross track
+error is the lateral distance between front axle center point (P\_\{x\},
+P\_\{y\}) and closest reference point (R\_\{x\}, R\_\{y\}) for which
+exponential can be shown\citep{ventures2006stanley}. This term helps the
+vehicle to steer towards the path to yield \(C_{e}\) as zero when its
+following the path. The heading error \(\theta_{e}\) is calculated by
+difference in vehicle heading \(\theta\) and reference heading
+\(\theta_{r}\) of path at \((R_{x}, R_{y})\). This term error directly
+apply to steering angle \(\delta\) with some steering angle limitation.
+
+\begin{equation}
+\label{eqn_heading_error}
+\theta_{e} = \theta - \theta_{r}
+%\caption{Heading error}
+\end{equation}
+
+When the cross track error \(C_{e}\) is non-zero, it adjusts \(\delta\)
+such that the intended trajectory intersects the reference path tangent
+from \((R_{x}, R_{y})\) at velocity in time \(V_{t}\) units from the
+front axle center point \((P_{x}, P_{y})\). The resulting steering
+control law by combining two terms are shown in equation
+\ref{eqn_stanley_equation} below. The figure \ref{fig_stanley}
+illustrates the geometric relationship of control parameters.
+
+\begin{equation}
+\label{eqn_stanley_equation}
+\delta(t) = k_{h}\theta_{e} + tan^{^{-1}}\left (\frac{k_{c}C_{e}(t)}{V_{x}(t)}  \right )
+\end{equation}
+
+Fig ?? shows a control error during simulation. A Stanley controller can
+be used for different type of course, such as parking, low speed, and
+medium travels.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.5in]{stanley_2.pdf}
+\caption{Stanley controller geometry}
+\label{fig_stanley}
+\end{figure}
+
+\section{Health Monitoring}\label{health-monitoring}
 
@@
 human safety must be prioritized in the system logic. Some components in
-the system that needs attention are listed in Table \ref{table_example}.
+the system that needs attention are listed in Table \ref{table_risk_hm}.
 
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{A Simple Example Table, IEEE standard format}
-\label{table_example}
+\caption{Risk in safety assessment for health monitoring module}
+\label{table_risk_hm}
 \centering

### 2016-01-21 ieee-pandoc-template/make_paper_tex.sh
added script to custom execute pandoc

@@ -1,0 +1,10 @@
+#!/usr/bin/zsh
+pandoc \
+	--standalone \
+	--natbib \
+	--smart \
+	--listings \
+	--template=./template_conf_multian.latex \
+	-H custom.latex \
+	--from=markdown \
+	metadata.yaml ./sections/main.md ./sections/other.md -o paper.tex

### 2016-01-23 ieee-pandoc-template/paper.tex
SUBMITTED TO IEEE IVS 2016

--- 2015-10-21 ieee-pandoc-template/paper.tex
@@
-%\documentclass[10 pt,letterpaper,conference]{IEEEtran}
-%\documentclass[10 pt,letterpaper,conference]{IEEEconf}
-\documentclass[10 pt,letterpaper,conference]{IEEEtran}
+\newcommand{\CLASSINPUTtoptextmargin}{104pt}
+\newcommand{\CLASSINPUTbottomtextmargin}{54pt}
+\newcommand{\CLASSINPUToutersidemargin}{37pt}
+\newcommand{\CLASSINPUTinnersidemargin}{54pt}
+
+%\renewcommand{\IEEEtitletopspaceextra}{18pt}
+%\documentclass[10 pt,a4paper,conference]{IEEEtran}
+%\documentclass[10 pt,a4paper,conference]{IEEEconf}
+\documentclass[10 pt,a4paper,conference]{IEEEtran}
 
@@
             pdfauthor={},
-            pdftitle={System Architecture for a Class of Small Service Vehicle},
+            pdftitle={Autonomous Service Vehicle Development for Urban Road Navigation},
             colorlinks=true,
@@
 \usepackage[numbers,square]{natbib}
-\bibliographystyle{IEEEtranN-nourl}
+\bibliographystyle{IEEEtranN}
 
 \usepackage{listings}
+
+\usepackage{algorithm}
+\usepackage{algorithmic}
+%\usepackage{algpseudocode}
+%\usepackage[]{algorithm2e}
+\usepackage{pifont}
+
+%\makeatletter
+%\algrenewcommand\ALG@beginalgorithmic{\footnotesize}
+%\makeatother
+
+\usepackage{tabularx}
+\usepackage{array}
 
@@
 
-\title{System Architecture for a Class of Small Service Vehicle}
+\renewcommand{\IEEEtitletopspaceextra}{18pt}
+%\title{Autonomous Service Vehicle Development for Urban Road Navigation}
+\title{\LARGE \bf Autonomous Service Vehicle Development for Urban Road Navigation}
 
 \author{
-		\IEEEauthorblockN{Saputra, V. B.}
+	\IEEEauthorblockN{
+		Saputra, V. B.\IEEEauthorrefmark{1}, 
+		Ravichandiran, B.\IEEEauthorrefmark{2}, 
+		Kumar Limbu, D.\IEEEauthorrefmark{6}, 
+		Wong, C. Y.\IEEEauthorrefmark{4} 
+		}
 	\IEEEauthorblockA{%
@@
 		1 Fusionopolis Way, Singapore 138632 \\
-	saputravb@i2r.a-star.edu.sg}
-	 \and
-		\IEEEauthorblockN{Ravichandiran, B.}
-	\IEEEauthorblockA{%
-		Institute for Infocomm Research \\
-		1 Fusionopolis Way, Singapore 138632 \\
-	ravib@i2r.a-star.edu.sg}
+		Email: (\IEEEauthorrefmark{1}saputravb  \IEEEauthorrefmark{2}ravib  \IEEEauthorrefmark{6}dklimbu  \IEEEauthorrefmark{4}cywong  ) @i2r.a-star.edu.sg
+	}
 }
@@
 \begin{abstract}
-By the dawn of the new millennium, robotics has undergone a major
-transformation scope and dimensions. This expansion has been brought
-about by the maturity of field and the advances in its related
-technologies. From a largely dominant focus, robotics has been rapidly
-expanding into the challenges of the world. The recent technology
-development demonstrated how the fast growing progress toward the of new
-perception, control, and motion planning techniques allow autonomous
-vehicles not only to travel significant distances in off-road, but also
-to operate in urban scenarios. The expected impact in the commercial
-sector for automotive manufacturers is equally if not more: autonomous
-sensing and control constitute key technologies to vehicles the future
-that might help save thousands of lives now lost in traffic accidents.
-Imagine a large field of vehicles without drivers traversing 60 miles in
-live, operating entirely without human guidance. A complex course
-including, traffic circles, and parking lots, defined by just kilobytes
-of data, several meters wide traveling down lanes only slightly wider,
-using systems with an accuracy of several meters. Humans in full-size
-unmanned vehicles at speeds up to 60 miles per hour. This actually would
-become reality in the near future. This project aims to bring the recent
-development on autonomous driving technology into a more practical and
-marketable platform so that it benefits can really be advantageous to
-real users.
+As the sensors and actuators for building an autonomous vehicle are
+getting increasingly affordable, both industry and research now could
+leverage on autonomous vehicle platform for various purposes. This paper
+presents a study of realizing a class of autonomous vehicle called
+Autonomous Service Vehicle (ASV) in the context of urban road
+navigation. The goal is to apply autonomous vehicle technology for human
+service oriented tasks. The ASV design is made for general service
+vehicle and it is intended to be reusable in term of hardware and
+software infrastructure. Components of the ASV are presented and
+experimentation was conducted to validate and evaluate the ASV. Further
+directions and necessary customization are explained in order to adapt
+the ASV design for various projects.
 \end{abstract}
@@
 
-\thanks{*This work was supported by Autonomous Vehicle Department, Institute for Infocomm Research}
-
 \section{Introduction}\label{introduction}
 
-The computational requirements for autonomous driving are very
-demanding, because autonomous vehicles have to process large amount of
-online and offline data in order to sense and understand their
-environment within long range safety distances with high precision, make
-and perform driving decisions at real-time. Most current autonomous
-vehicle prototypes around the world employ powerful distributed systems
-consisting of multiple heterogeneous processors and systems for sensory
-data processing, sensor fusion, intelligent behavior, and driving
-control. These types of prototype systems are bulky, costly and power
-hungry, thus are not suitable for real world deployment. Recently, Audi
-developed an all-in-one embedded platform code named zFAS which
-incorporates multiple heterogeneous processors (ECU/MCUs, Application
-Processors, GPUs, FPGA and a video detection subsystem) on a single
-tightly integrated board with specialized communication architecture
-(including Deterministic Ethernet) to suit autonomous driving needs. The
-computing power equals to the entire electronics architecture of today's
-Audi vehicles, yet at a fraction of the size, cost and power
-consumption. Such a platform is invaluable to eventually bring
-autonomous driving technologies to the mass market.
+Recent advancements in robotics technology have brought great benefit to
+autonomous vehicle research. Since the Defense Advanced Research
+Projects Agency (DARPA) 2003 Grand Challenge
+\citep{ventures2006stanley}, many research groups have focused their
+effort to solving problems related to autonomous vehicle navigation. As
+laboratories and research centers bringing the autonomous vehicle
+technologies to real world applications \citep{Ford_Jan_16}, acceptance
+of fully unmanned vehicles will still be a challenge. However, with
+current progress it can be shown that for a specific problem domain, in
+this case service vehicles, the autonomous vehicle can be utilized for
+automation of human service oriented tasks, such as automated road
+cleaning, grass cutting and leaves sucking machine. This is supported by
+the growth of service robotics industry in the recent years
+\citep{SVR_Nov_15}. \citeauthor{7225673} \citep{7225673} introduced
+mobile service robot for electrical power plant inspection. This in turn
+could reduce or replace human involvement in manual inspection process.
+\citeauthor{6629559} \citep{6629559} presented an autonomous driving car
+for research purposes that includes features that allows for urban road
+navigation. Similarly, \citeauthor{7225765} \citep{7225765} introduced a
+more advanced autonomous driving platform consisting of high performance
+cameras, LIDARs, and other navigation sensors. While these platforms are
+very attractive in term of their capability of handling big streams of
+sensors data, the demanding computing power renders them unsuitable for
+small service vehicle. The Autonomous Service Vehicle (ASV) proposed in
+this paper is developed as a prototype to demonstrate autonomous vehicle
+capability tasked for a service vehicle.
 
-This paper aims to describe and propose a generic design of the system
-architecture based on the chosen compute components and the
-characteristics / requirements of sensor fusion and autonomous driving
-applications, integration, test and characterization for a class of
-small service vehicle.
+Autonomous platforms are usually retrofitted from manually driven
+vehicles. This approach is commonly used because it is the most viable
+and affordable way to install a Drive-By-Wire (DBW) system into existing
+vehicle rather than to entirely build a new one. It was also studied
+that automation driver's task has positive impact to improving driving
+safety \citep{stanton1996fly}. Various effort to assist drivers has lead
+to development of ADAS system \citep{6232125, 7225760}. A DBW enables
+computerized control of the vehicle by means of replacing human drivers
+with actuators, which are usually driven by electrical motors
+\citep{1035218}. The ASV presented in this paper is retrofitted from a
+compact electric vehicle \citep{SongZW_IV_2015}, and thus we studied the
+feasibility of converting this class of vehicles into service vehicles.
+
+This paper contribution is threefold. First, to describe and propose a
+generic design of the system architecture based on necessary components
+for the ASV applications. Second, to propose the ASV architecture to be
+adopted into generic service platform for both research and application
+purposes. Although, the implementation of the ASV presented here are
+subject to certain sources, the components are generic and should be
+reproducible with similar effort. Lastly, to present discussion on
+issues surfaced during tests and evaluation of the ASV navigation in
+urban road environment.
 
@@
 
-Components of a typical autonomous or assistive driving system could be
-summarized in Fig. \ref{fig_1}. The system heavily depends on various
-types of sensory data and sensors of the same type are synced with one
-another through data sync modules. To make sense of sensor data, raw
-data processing is required for different types of available data.
-Overlapping field of views from different sensors could be combined and
-the processing result is fused through a Low Level Fusion module. This
-module also does some filtering to eliminate local noises and thus, make
-the information more robust to small disturbances. The output objects
-and localization data from low level fusion modules are then sent to a
-High Level Fusion Module whereby all objects and filtered sensor
-information are fused together to form a world model.
+The main service types for ASV are related to defense, agriculture and
+inspection, logistics and medical applications \citep{SVR_Nov_15}. As a
+platform, ASV is required to navigate through environment to complete
+the assigned service tasks. The approach taken is to modify current
+vehicle to enable automated control by means of processing sensors data.
+In this paper, the ASV components are designed to complete a case of
+urban road navigation. Components of the proposed ASV can be summarized
+in Fig. \ref{fig_1}.
 
@@
 \centering
-\includegraphics[width=2.5in]{HighLevel.pdf}
-\caption{Block Diagram of an autonomous vehicle driving system.}
+\includegraphics[width=3.5in]{ecoms_arch.pdf}
+\caption{Block Diagram of the ASV system.}
 \label{fig_1}
@@
 
-{[}XME? Please fill in{]}
+Middleware refers to the software component that connects the various
+modules across network of distributed system. It makes communication
+transparent to connected modules by providing reliability, consistency,
+security, and privacy capabilities. In the ASV architecture CHROMOSOME
+(abbreviated as XME) \citep{CHROMOSOME}, a message-oriented middleware
+is used. XME implements the publish-subscribe message paradigm, which
+provides guarantees with respect to the behaviour of distributed
+applications \citep{buckl2014chromosome}. The other alternative
+middlewares are Robotics Operating System (ROS) \citep{quigley2009ros}
+and OpenRTM-aist \citep{ando2005rt} which are commonly used in the field
+of robotics.
 
-\section{Components}\label{components}
+\subsection{Localization}\label{localization}
 
-\subsection{Drive-By-Wire}\label{drive-by-wire}
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.5in]{localize_2.pdf}
+\caption{Feature Detection and Particle Filter of Localization process.}
+\label{fig_localize}
+\end{figure}
+
+As opposed to indoor localization, the environment where ASV usually
+deployed is outdoor and GPS data is available. However, it is studied
+that GPS data is often contain errors that is too large for autonomous
+navigation \citep{6629559}. One approach to compensate the error is to
+use local lane marker or road boundary information to adjust lateral
+position of the vehicle with respect to the road \citep{loc_Boss}. This
+allow the vehicle control to always offset the vehicle position to
+always stay on the drivable area on the road. However, it can be argued
+that the position in longitudinal direction along the road with this
+approach is not accurate. For service applications, it is necessary that
+both lateral and longitudinal position of the vehicle are determined
+accurately as the ASV often need to stop at specific point in its route.
+We developed a hybrid approach that fuses both information from GPS and
+a prior map based online localization. The method is based on Particle
+Filter or sequential Bayes filter that involves prediction from vehicle
+motion model and measurement update cycle \citep{6550131}. The
+measurement update computed from GPS and the feature scan matching. This
+approach is suitable for service applications because the size of the
+map is ranging from small to medium scale up to a few kilometer squares.
+With the current computing technology, the map of this size can be fully
+loaded into memory.
+
+Before deployment, the ASV needs build its feature map by collecting
+data during manual driving. A map is built by aggregating the data from
+laser range sensors installed in the ASV. This is implemented in
+two-staged process. In the first stage, raw scan data is collected and
+sequentially aligned with an Iterative Closest Point (ICP) method
+\citep{censi08plicp}. During alignment, raw point cloud map is built by
+registered point cloud and any loop closure will improve consistency of
+the detected vehicle positions during mapping \citep{tiar2015fast}. In
+the second stage, features along lateral and longitudinal direction are
+gathered and registered into processed feature map. The dominant
+features used for urban environment are road curbs and tree trunks. The
+result of feature detection, and the ASV Particle Filter map based
+localization can be shown in Fig. \ref{fig_localize}.
+
+\subsection{Obstacle Detection}\label{obstacle-detection}
+
+During operation of the ASV, obstacle obstructing or near the vehicle
+should be considered. Thus, by using a laser range sensor model for
+detection, a set \(L\) of \(n\) points which each has a range \(r_{i}\)
+and a angle \(\alpha_{i}\), measured from laser beams
+\(L=\left\{(r_{1},\alpha_{1}),...,(r_{n},\alpha_{n})\right\}\) are
+clustered to extract objects \citep{Juric-Kavelj2008_407}. A Gaussian
+smoothing is applied to remove spurious noise before processing. Two
+subsequent points belong to one cluster satisfies the distance threshold
+\(d(r_{i},r_{i+1}) \leq D_{0}+D_{1}min(r_{i},r_{i+1})\), where \(D_{0}\)
+is the accuracy of the range data.
+\(D_{1} = \frac{3}{2}(\alpha_{i+1}-\alpha_{i})\) is a constant that
+determine maximum change allowed. Point that break the threshold will be
+the start of another cluster. Processed laser scanner is represented by
+a set of clusters \(\left\{ C_{1},...,C_{m} \right\}\). Each cluster
+consists of tuples
+\(({}^{C}r_{i},{}^{C}\alpha_{i},{}^{C}x_{i},{}^{C}y_{i})\) where
+\({}^{C}x_{i}\), \({}^{C}y_{i}\) are the Cartesian coordinate
+representations.
+
+Each cluster is a potentially detected object. Based on the lateral
+proximity of each cluster, object boundaries are found by determining if
+each cluster satisfies \(w_{min} \leq d(y_{min},y_{max}) \leq w_{max}\),
+where \(w_{max}\) and \(w_{min}\) depend on widths of object of
+interest. The detected obstacles are sent the path planner to aid in
+calculation of the navigation course. Moreover, obstacle detection
+improves false recognition removal of map objects for localization
+\citep{5164269}. The cluster points of detected objects are used to
+determine areas of where measured points should be excluded from the
+localization and mapping process.
+
+\subsection{Path Planning}\label{path-planning}
+
+The Path planning module generate reference trajectory for the ASV to
+follow from a start to a destination point. The ASV path planning is
+implemented in two stages: Global Path Planning and Local Path Planning.
+
+\subsubsection{Global Path Planning}\label{global-path-planning}
+
+Global path planning aims to generate the waypoints to connect the
+destination and the start point. In the literature, global path planning
+can be achieved by the notable path planning algorithm such
+\(A^{*}\)\citep{hart1968formal}, \(D^{*}\)\citep{stentz1994optimal},
+Rapidly-Exploring Random Trees\citep{lavalle1998rapidly}, Probabilistic
+roadmaps\citep{kavraki1996probabilistic}. For the ASV, a teach and
+repeat solution is prefered as the planned path rarely change. This
+implies that once the ASV is taught to navigate through certain
+waypoints, it will be able to repeat it and more complex routing can be
+achieved by combining multiple sets of waypoints. The ASV obtain its
+trajectory by recording the vehicle position provided by localization
+during manual driving. The trajectory obtained is further optimized by
+post processing Alg. \ref{alg_global_waypoints}. In post processing
+duplicate vehicle position points, points lie on straight line, curved
+points within vehicle turning radius are removed to generate the
+optimized path.
+
+\begin{algorithm}
+      \scriptsize
+      \algsetup{linenosize=\scriptsize}
+      \caption{Global Path Planning}
+      \label{alg_global_waypoints}
+      \begin{algorithmic}[1]
+          \REQUIRE minLen, minRad, recordedPoint[] \COMMENT{array contains x, y and $\theta$}
+            \STATE initialize points[], globalPoints[] \COMMENT{array contains x, y and $\theta$}
+
+            \STATE totalGlobalPoints = 0
+
+            \FORALL{$points$ in $recordedPoint$}
+                \IF{$totalGlobalPoints$ == 0}
+                    \STATE append $points$ to $globalPoints$
+                    \STATE $totalGlobalPoints++$
+                \ELSE
+                    \IF{((distance between $points$  and $globalPoints[totalGlobalPoints - 1]$) $\geq$ $minLen$) $\AND$ (($\arctan$ between $points$ and $globalPoints[totalGlobalPoints - 1]$) $\geq$ minRad)}
+                        \STATE append $points$ to $globalPoints$
+                        \STATE $totalGlobalPoints++$
+                    \ENDIF
+                \ENDIF
+            \ENDFOR
+      \end{algorithmic}
+\end{algorithm}
+
+\subsubsection{Local Path Planning}\label{local-path-planning}
+
+Local Path Planning aims to generate dynamic reference trajectories with
+vehicle dynamics constraints such as turning radius and maximum
+velocity. Based on Global Path Planning trajectory, Local Path Planning
+is recursively generated during vehicle on motion with specified
+interval to achieve smoother vehicle navigation. Local Path Planning
+mainly helps to deal with dynamic circumstances, such as avoiding
+obstacle along the global path and to perform smoother turning based on
+velocity constraint. The Local Path Planning module is developed with
+Dubins-Curve \citep{DubinsCurves} library which is based Dubins
+\citep{dubinscurve1957} path method. Dubins path is one of the simplest
+geometric methods to compute the shortest path between two points in the
+Euclidean plane with turning radius as constraint. Dubins path is
+suitable for nonholonomic wheeled mobile robot or car like autonomous
+vehicles. Dubins path is built on top of the assumption that
+non-holonomic vehicle has a typical motion of going straight (S),
+turning left(L) and turning right(R). According to Dubins
+\citep{dubinscurve1957} optimal path will be always one of the six
+possible motion sequences: \{LSL, RSR, RSL, LSR, LRL, RLR\}. For details
+on Dubins method, readers can refer to section 15.3.1 in
+\citep{lavalle2006planning}. Local Path Planning Alg.
+\ref{alg_local_waypoints} is executed at regular interval when the AVS
+has travelled a certain distance or any obstacle is detected along the
+path. In the event of obstacle obstructing the global path, the local
+path will be shifted to the left or right side of obstacle boundary
+based on environmental factors for safer avoiding. However, if the
+obstacle is an moving object, the planner is unable to avoid. Thus, in
+this case velocity profile will be lowered down based on a safe distance
+threshold. An example of the Local Path Planning avoidance is shown on
+Fig. \ref{veh_avoid_close}.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.0in]{vehicle_travelled_crop.pdf}
+\caption{Vehicle avoidance path generated by local path planning}
+\label{veh_avoid_close}
+\end{figure}
+
+\begin{algorithm}
+      \scriptsize
+     \algsetup{linenosize=\scriptsize}
+
+      \caption{Local Path Planning}
+      \label{alg_local_waypoints}
+      \begin{algorithmic}[1]
+          \REQUIRE currentPos, obstaclePoints[], globalPoints[], turnRadius, stepSize, maxLen
+            \STATE initialize localPoints[], startPoint[], endPoint[] \COMMENT{array contains x, y and $\theta$}
+            \STATE wayLen = 0
+
+            \STATE $globalClose \leftarrow$ Find closest $globalPoints$ to $currentPos$ \COMMENT{closest points based on Euclidean distance}
+
+            \STATE $startPoint$ = $globalPoints[globalClose]$
+
+            \WHILE{$startPoint$ is not a last globalPoint $\AND$ $wayLen \leq maxLen$ }
+
+                \STATE $endPoint$ = $globalPoints[startPoint + 1]$
+
+                \IF{$obstaclePoints$ exists between $startPoint and endPoint$}
+                \STATE $endPoint \leftarrow$ will be shifted point where obstaclePoint exist. \COMMENT{Based on environment path shift will either left or right}
+                \ENDIF
+
+                \STATE $wayLen \leftarrow$ add Dubins Path Length for $startPoint$ and $endPoint$
+                \STATE $localPoints \leftarrow$ append Dubins Path for $startPoint$ and $endPoint$ with given $turnRadius$ and $stepSize$
+                \STATE $startPoint$ = $endPoint$
+            \ENDWHILE
+
+      \end{algorithmic}
+\end{algorithm}
 
@@
 
-Fig \ref{fig_2} shows a control error during simulation. A Stanley
-controller can be used for different type of course, such as parking,
-low speed, and medium travels.
+Vehicle control performs necessary action to follow the intended path
+generated by path planner for smooth navigation towards destination
+point. The gas and brake control for regulating vehicle velocity along
+longitudinal direction will be handled by the velocity control module.
+The steering control for turning vehicle along lateral direction will
+handled by the lateral control module.
+
+\subsubsection{Velocity control}\label{velocity-control}
+
+Velocity control controls the vehicle velocity for along longitudinal
+direction by controlling the gas, brake motor position in the drive by
+wire system. Velocity control aims to achieve the desired velocity
+determined by the module's input such as path planning, obstacle
+detection and health monitoring report. For smoother control and to
+avoid jerkiness of the vehicle, speed profiling is needed. Speed
+profiling is the process to estimates the speed based on the curvature
+of the path and speed limits for specific environments along vehicle
+trajectory. The estimation is calculated from the aggregation of the
+data collected during manual driving and maximum/minimum speed limits
+are applied. During local path planning, speed profiling is computed to
+determine the optimal speed.
+
+To achieve the desired velocity, a closed loop
+Proportional-Integral-Derivative (PID) controller is implemented to
+compute the desired gas/brake position of the DBW motor. The closed loop
+PID controller helps in noise rejection and robustness of control with
+design flexibility. Based on desired velocity, the controller will
+calculate the motor position and passes to drive by wire (DBW) system.
+The wheel encoder measures the speed precisely and provide feedback to
+the controller. The block diagram of the velocity control implementation
+is shown in Fig \ref{fig_vel_control}. The governing control law of the
+PID controller is given in the following:
+
+\begin{equation}
+\label{eqn_pid}
+GB = k_p{E} + k_{i}\int_{0}^{t}{E}\,{dt} + k_{d}\frac{dE}{dt}
+\end{equation}
+
+Where \(GB\) is gas-brake position value, \(E\) is the velocity error,
+\(dE\) is the differential error, \(k_p\) is the proportional gain,
+\(k_i\) is the integral gain, \(k_d\) is the differential gain.
 
@@
 \centering
-\includegraphics[width=2.5in]{fig_ex.pdf}
-\caption{Example of matplotlib graph (vector graphic in the paper).}
-\label{fig_2}
+\includegraphics[width=3.5in]{pid_velocity.pdf}
+\caption{Velocity control based on closed loop PID.}
+\label{fig_vel_control}
 \end{figure}
 
-\subsection{Path Planning}\label{path-planning}
+\subsubsection{Lateral Control}\label{lateral-control}
 
-Path planning done by \citeauthor{SongZW_IV_2015} has revealed the fact
-that small service vehicle can be robustly navigate the path as long as
-the localization gives its correct position. For more examples, readers
-are encouraged to read \citep{Corley-etal_2011}. In addition,
-\citet{Corley-etal_2012} confirmed that localization can be affected by
-surrounding dynamic environment changes such as parked cars, and moving
-pedestrians. \citet{Aalst-etal_2004} proposed a solution to this, but
-later the work has been verified not working in
-\citep{Abadi-etal_2008, Abebe-etal_2009}. For more references on this
-problem, suggested readings are
-\citep{Ackerman-Halverson_1998, Agrawal-etal_1998, Ali-etal_2012, Alipour-etal_2013}.
-
-\subsection{Mapping}\label{mapping}
-
-Procedure of mapping includes:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Point cloud assembly
-\item
-  Point cloud registration
-\item
-  Extracting useful information
-\end{enumerate}
-
-\subsubsection{Point cloud assembly}\label{point-cloud-assembly}
-
-The assembly process is aggregating several point cloud frames from
-sensor scans with some process of point cloud matching and registration.
-
-\subsubsection{Point cloud registration}\label{point-cloud-registration}
-
-\subsubsection{Extracting useful
-information}\label{extracting-useful-information}
-
-\begin{itemize}
-\tightlist
-\item
-  Road curb
-\item
-  Traffic signs/lights
-\item
-  Building features
-\end{itemize}
-
-\paragraph{Road curb}\label{road-curb}
-
-Road curb is the most reliable feature in road boundary detection. It is
-easy to detect and currently it is the baseline for localization.
-
-\paragraph{Traffic signs/lights}\label{traffic-signslights}
-
-\paragraph{Building features}\label{building-features}
-
-\subsection{Localization}\label{localization}
-
-The localization is done by modeling the problem using \emph{Gamma
-function} satisfying \(\Gamma(n) = (n-1)!\quad\forall n\in\mathbb N\) is
-via the \textbf{euler} integral:
+Lateral control aims to control the steering angle of the vehicle based
+on trajectory generated by path planner. The lateral controller is
+developed based on Stanley's \citep{ventures2006stanley} steering
+controller. Stanley steering controller is the geometric path tracking
+approach used by Stanford university's autonomous vehicle during DARPA
+grand challenge 2006. The closed-loop geometric tracking controller
+helps vehicle to follow the desired path generated by local path
+planning. The controller is based on non-linear cross track error
+\(C_{e}\) and heading error \(\theta_{e}\). Cross track error is the
+lateral distance between front axle center point \((P_{x}, P_{y})\) and
+closest reference point \((R_{x}, R_{y})\) for which exponential can be
+shown \citep{ventures2006stanley}. This term helps the vehicle to steer
+towards the path to yield \(C_{e}\) as zero when its following the path.
+The heading error \(\theta_{e}\) is calculated by difference in vehicle
+heading \(\theta\) and reference heading \(\theta_{r}\) of path at
+\((R_{x}, R_{y})\). This error term directly applies to steering angle
+\(\delta\) with some steering angle limitation.
 
 \begin{equation}
-\label{eqn_example1}
-x = \sum\limits_{i=0}^{z} 2^{i}Q
+\label{eqn_heading_error}
+\theta_{e} = \theta - \theta_{r}
 \end{equation}
 
+When the cross track error \(C_{e}\) is non-zero, it adjusts \(\delta\)
+such that the intended trajectory intersects the reference path tangent
+from \((R_{x}, R_{y})\) at velocity in time \(V_{t}\) units from the
+front axle center point \((P_{x}, P_{y})\). The resulting steering
+control law by combining the two terms are shown in
+(\ref{eqn_stanley_equation}). \(k_{h}\) and \(k_{c}\) are the gain
+constants for heading error and cross error, respectively. Fig.
+\ref{fig_stanley} illustrates the geometric relationship of control
+parameters.
+
 \begin{equation}
-\label{eqn_example2}
-\Gamma(z) = \int_0^\infty t^{z-1}e^{-t}dt\,.
+\label{eqn_stanley_equation}
+\delta(t) = k_{h}\theta_{e} + tan^{^{-1}}\left (\frac{k_{c}C_{e}(t)}{V_{x}(t)}  \right )
 \end{equation}
 
-\begin{equation}
-\label{eqn_example3}
-\mathbf{V}_1 \times \mathbf{V}_2 =  \begin{vmatrix}
-\mathbf{i} & \mathbf{j} & \mathbf{k} \\
-\frac{\partial X}{\partial u} &  \frac{\partial Y}{\partial u} & 0 \\
-\frac{\partial X}{\partial v} & \frac{\partial Y}{\partial v} & 0
-\end{vmatrix}
-\end{equation}
+\begin{figure}[!t]
+\centering
+\includegraphics[width=1.5in]{stanley_2.pdf}
+\caption{Stanley controller geometry}
+\label{fig_stanley}
+\end{figure}
 
-Equation (\ref{eqn_example2}) is convoluted by means of \emph{Gaussian
-Distribution}. In other words, (\ref{eqn_example1}) depicts the spectrum
-of (\ref{eqn_example2}). The \textbf{eigen }matrix for the point cloud
-distribution is given in (\ref{eqn_example2}).
-
-\section{Safety Consideration}\label{safety-consideration}
+\subsection{Health Monitoring}\label{health-monitoring}
 
@@
 service vehicle. Not only that robust operation is required, but also
-human safety must be prioritized in the system logic. Some components in
-the system that needs attention are listed in Table \ref{table_example}.
+safety must be prioritized in the event of malfunctions or catastrophic
+failures. Health monitoring module is a component in the ASV that acts
+as a safety agent to react to those events in timely manner. It is based
+on publish-subscribe model. This allows both centralized and distributed
+monitoring model. In the initialization stage, each ASV functional
+module component subscribes to a health topic proceeding completion of
+self-diagnosis. The health topic is provided by the Central Health
+Monitor (CHM). In the operational stage, modules are to send unique
+description and event identification with timestamp to the CHM. The CHM
+is responsible for reporting any important event to the user, log the
+event, and take suitable action based on severity of the detected
+failure or error. In addition, each module has their own reporting
+module, but limited only to each module scope of operation. The severity
+levels and the corresponding actions can be summarized in Table
+\ref{table_risk_hm}.
 
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{A Simple Example Table, IEEE standard format}
-\label{table_example}
+\caption{Severity Level in Health Monitoring}
+\label{table_risk_hm}
 \centering
-\begin{tabular}{c||c}
-\hline\bfseries Component & \bfseries Risk\\
+\footnotesize
+\begin{tabular}{p{1.5cm}||p{6.cm}}
   \hline
-\hline Drive-By-Wire & Malfunction of motors\\
+    \textbf{Severity} &
+    \textbf{Actions} \cr
+  \hline\hline
+    None & Normal Operation. Status Logging. \cr
   \hline
-\hline GPS & GPS denied\\
+    Warn & Display warning on user interface. Status logging. \cr
   \hline
-\hline Camera & Cable loose\\
+    Abort & Vehicle aborts mission, plans and stops at a safe zone. Status logging and displaying on user interface. \cr
+  \hline
+    Emergency Stop & Vehicle aborts mission immediately. Status logging and displaying on user interface. All modules restart and perform self-diagnosis. \cr
   \hline
@@
 
-\section{Experimentation}\label{experimentation}
+\subsection{Human Machine Interface}\label{human-machine-interface}
 
-Fig. \ref{coms1_bare} shows the first vehicle platform that we first
-retrofitted for the autonomous vehicle project.
+Human Machine Interface (HMI) is a graphical user interface where users
+could control and monitor the ASV. We have developed a web based HMI, so
+that the ASV could be monitored and controlled from any remote location.
+Remote control functions include emergency stop immediate request, task
+scheduling and change or reroute the ASV global path plan. The HMI is
+web based and developed with websocket \citep{fette2011websocket}
+protocol implementation for achieving low-latency, long-running
+bidirectional communication. For security concern, HMI can be accessed
+only from intranet with unique private IP assigned for the ASV and user
+need to authenticate with username and password. Any HTML5 supported
+browser can be used to access the HMI. The HMI consist of dashboard,
+system interface and settings interface. They individually has different
+scope of information and options. For example, Fig. \ref{fig_hmi} shows
+the HMI dashboard. The dashboard is essential for vehicle monitoring
+information such as precise ASV position on the map, vehicle speed,
+battery level and system log for displaying critical error logs and
+network status. The system interface is used to manage individual
+modules. It has options to starting, to stop and to view error logs. The
+settings interface is used to modify ASV parameters such as maximum
+speed, braking distance, velocity control and lateral control gain.
 
@@
 \centering
-\includegraphics[width=2.5in]{coms1_bare}
-\caption{Experimentation of building vehicle platform.}
+\includegraphics[width=3.0in]{hmi.pdf}
+\caption{HMI dashboard interface}
+\label{fig_hmi}
+\end{figure}
+
+\section{Experimentation}\label{experimentation}
+
+In our previous work \citep{SongZW_IV_2015}, we retrofitted the first
+version of a compact electric vehicle. In this paper, we upgraded the
+ASV system and improve installation by moving into the second version of
+the vehicle. The second version vehicle provides better stability in
+term of maneuverability, and provide more space at the back of passenger
+seat to install complete power supply system and necessary computing
+devices. The current ASV prototype is shown in Fig. \ref{coms1_bare}.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[height=1.7in]{coms2_1.pdf}
+\caption{Vehicle platform for the ASV.}
 \label{coms1_bare}
@@
 
-\subsection{Sensors}\label{sensors}
+\subsection{Setup}\label{setup}
 
-Placement of the sensors on the autonomous vehicle can be seen in Fig.
-\ref{ipe_ex}, and their connection to the system can be summarized in
-Fig. \ref{dia_ex}.
+Placement of the components on the autonomous vehicle can be seen in
+Fig. \ref{ipe_ex}, and their connection to the system can be summarized
+in Fig. \ref{dia_ex}. As can be seen, the vehicle has a dedicated box
+originally tailored for carrying load. This box is revamped so that it
+has more space to contain all the components. The ASV system is
+integrated through a Central Processing Unit (CPU) and a Sensor Actuator
+Hub (SAH). Both CPU and SAH are compact PCs, but for different purpose.
+All the modules including HMI and CHM are run on the CPU. SAH gathers
+data from sensors and from the Vehicle Interface (VI). On top of that,
+it also bridges the CPU with the DBW control and emergency stop signal
+can bypass control to instruct immediate brake. In order to provide
+real-time logging and a database server system is installed in a low-end
+compact PC. This log database server receives data from all modules, and
+writes to storage in timely manner so that in the event of sudden power
+loss or vehicle breakdown, most recent data can be recovered and
+analyzed.
 
@@
 \centering
-\includegraphics[width=2.5in]{ipe_ex.pdf}
-\caption{Placement of sensors.}
+\includegraphics[height=1.6in]{ipe_ex.pdf}
+\caption{Placement of components in the ASV.}
 \label{ipe_ex}
@@
 \centering
-\includegraphics[width=2.5in]{dia_ex.pdf}
-\caption{Diagram of sensors connection.}
+\includegraphics[width=1.9in]{dia_ex.pdf}
+\caption{Diagram of components connection.}
 \label{dia_ex}
@@
 
+\subsubsection{Drive-By-Wire}\label{drive-by-wire}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.5in]{Overview.jpg}
+\caption{Drive-by-Wire installation of the ASV.}
+\label{fig_DBW}
+\end{figure}
+
+The original vehicle comes with steering and gas/brake pedals. The
+Drive-By-Wire (DBW) refers to the mechanics added on to the vehicle so
+that it can be controlled by computer. Two motors are installed, each
+for controlling the steering and the pedals. The steering actuation is
+achieved by modifying the steering column and combining it with the
+steering motor shaft. The pedals actuation is designed so that only one
+pedal is pressed at one time. This actuation is achieved by installing
+two levers on top of each pedal, and connecting them to the second
+motor: one lever via direct linkage, and the other lever via a metal
+wire in such a way that individual pedal can be pressed by selecting
+motor rotating direction. This removes the need for a third motor, and
+also increases safety that it is mechanically impossible to press both
+pedals in case there is error in the motor controller. The electric
+vehicle only has two gear options linked directly to the internal motor
+inverter as it does not have mechanical gear, but the gear is needed to
+determine the direction of travel. Thus, the gear selection can be
+controlled using electrical signal through the VI.
+
+\subsubsection{Power Distribution}\label{power-distribution}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.2in]{power_diagram.pdf}
+\caption{Electrical diagram of the ASV.}
+\label{fig_power}
+\end{figure}
+
+The power supply for the CPU, DBW, sensors and other peripherals is
+provided by a separated rechargeable Lithium Polymer (LiPo) batteries.
+The autonomous operation runs independently on the LiPo batteries to
+avoid complication that may arise if the main batteries is tapped.
+Furthermore, power supply for ASV is crucial as the autonomous system
+depends on it. Therefore, additional Power Supply Units (PSU) and a UPS
+are installed such as shown in Fig. \ref{fig_power}. There are multiple
+redundancies power line to secure fail-safe and fault-tolerant operation
+of the ASV during its navigation. In addition, VI unit is made of
+multiple stack of microcontroller and relay boards in order to ensure
+safe interfacing to/from the vehicle. Fans are installed to provide
+regulate temperature inside the box.
+
+\subsubsection{Sensors}\label{sensors}
+
+Autonomous navigation of the ASV heavily depends on the perception
+system which data comes from various sensors.
+
+\paragraph{Odometry}\label{odometry}
+
+Odometry position is estimated via accumulating the motion sensors data
+over time. Pure odometry position is not recommended for long-term
+navigation, since the motion sensor error will accumulate drift in the
+actual position over time. The navigation relies on the localization
+module to fuse odometry data with GPS data and the developed map based
+localization. The odometry position is derived from the equation
+\ref{eqn_simple_odometry}. The following two motion sensors are
+installed in the ASV: a wheel motion sensor (Kistler Wheel Pulse
+Transducers) to calculate vehicle travelled distance, and GPS/IMU sensor
+(Xsens MTi-G-700 GPS) to measure global positions and heading rate.
+
+\begin{equation}
+\begin{split}
+\label{eqn_simple_odometry}
+\theta_t = \theta_{t-1} + \Delta\theta_{t} \\
+x_t = x_{t-1} + (\Delta v_t + cos(\theta_t)) \\
+y_t = y_{t-1} + (\Delta v_t + sin(\theta_t))
+\end{split}
+\end{equation}
+
+where \(\Delta\theta\) is the yaw rate obtained from IMU, \(\theta\) is
+the heading, \(\Delta v\) is distance obtained from wheel motion sensor,
+\(x\) and \(y\) are the Cartesian coordinates of the odometry position,
+and \(t\) is the time index which is increased every sampling time.
+
+\paragraph{Laser Range Sensors}\label{laser-range-sensors}
+
+LIDAR ( Light Detection and Ranging) is one of the popular light range
+sensors used in various field of Robotics, Autonomous Vehicles, and
+Geo-mapping, forestry, etc. LIDAR will provide the distance of the
+object by emitting laser towards it and analysing its reflection.
+Compared to stereo vision systems \citep{6856563}, LIDARs generally has
+more field of view, longer detection range, and more accurate depth
+information. A four layers Lidar (Ibeo ScaLa) is mounted on front bumper
+facing forward for obstacle detection up to 100 meters. The obstacle
+detection can be done in one layer, but the other layers will provide
+redundancies if the ASV tilt forward or backward. In this case, one or
+more layers can hit the ground or the free space below or above an
+object, respectively. At least one layer will detect an object if there
+is one. Another 16 layers Lidar (Velodyne Puck) which can sense
+surrounding object and environment shape in 25m radius is used mainly
+for localization. This LIDAR is mounted roughly \(30^{\circ}\) towards
+ground purposely for detecting main features of the environment such as
+the road curbs and the tree trunks which are used for localization.
+
+\paragraph{Camera}\label{camera}
+
+The camera (Logitech C930e) is used for video data logging and remote
+monitoring via the HMI interface. Camera video frames are read using
+\emph{video4linux} API, which later encoded and streamed in \emph{WebM}
+format with \emph{ffmpeg} and \emph{ffserver} setup. We did try to use
+image processing to detect lane marker for navigation, but unfortunately
+due to shadows and significant change in ambient light level during the
+day, detection results were not stable. This issue can be solved by
+replacing the camera with HDR camera or fuse the results with the LIDAR
+point cloud intensity data.
+
+\subsubsection{Safety System}\label{safety-system}
+
+Safety is a primary concern for any autonomous system, AVS should be
+stopped safely in any unexpected circumstances, such as sensor failures
+or errors in software modules. In the AVS experiment, we have
+implemented safety in three levels. First level is implemented in the
+Health Monitoring system which monitors hardware, software modules and
+takes necessary action on failures reported. The on-board emergency
+switch which provides the second level of safety, can be accessed while
+there is a person inside the ASV. Third level is implemented by a remote
+software emergency stop through the HMI interface and a hard-wired radio
+emergency stop system which works on 900MHz and 2.4GHz frequency.
+
+\subsection{Testing Results and
+Evaluation}\label{testing-results-and-evaluation}
+
+Testing is carried out in an urban environment for the distance of 1km
+range. As explained in the global path planning, waypoints record by
+manual driving and processed. Figure \ref{map_waypoint} shows the map of
+the urban environment road structure and global trajectory for testing.
+For autonomous driving, the maximum velocity is capped by 4m/s and
+static obstacles are placed in 3 locations as shown on Fig.
+\ref{veh_path_overview}. Figure \ref{vel_error_test} shows the output of
+velocity control with respective to desired velocity. Velocity
+controller achieves desired velocity linearly and little noise is also
+observed during constant velocity. Between 900 to 950 cycle time there
+is a sudden drop of velocity is noticed, which is caused by dynamic
+obstacle along the path that caused the vehicle to slow down. However,
+the ASV velocity controller can recover speed to the desired profile
+after the object is no longer detected.
+
+Figure \ref{control_error_test} shows the output of lateral control such
+as angle error, lateral distance error (cross-track error) and final
+steering output. The control parameter of the ASV is tuned to tolerate
+localization error up to 20 cm, thus the final steering output follows
+angle error closely unless there is a steady-state lateral distance
+error. This can be seen that eventhough the localization emits episodic
+high-frequency noisy data due to bad perception or GPS signal, the
+controller is able to filter the steering output. This results in smooth
+driving experience if someone is inside the ASV. In the event of turning
+in a higher error is observed. This is due to maximum steering
+constraint which is set to 0.41 radians. Errors during turning is
+expected to turn the steering to the direction of the path.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.5in]{map_overlay.pdf}
+\caption{Recorded Waypoint to travel}
+\label{map_waypoint}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.5in]{vehicle_travelled_label.pdf}
+\caption{Vehicle path overview}
+\label{veh_path_overview}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.5in]{velocity_error_1.pdf}
+\caption{Velocity Control output during testing }
+\label{vel_error_test}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.5in]{control_error_1.pdf}
+\caption{Lateral Control output during testing }
+\label{control_error_test}
+\end{figure}
+
+\subsection{Adaptation for specific
+service}\label{adaptation-for-specific-service}
+
+Depending on the specific task, various tools which include sensors
+and/or actuators that are necessary for the service task can be mounted
+onto the ASV. These sensors and actuators are collectively called as a
+workload. The ASV modules are customizable to carry the workload and
+perform the desired service task. The ASV localize itself by using
+information from map and GPS, thus eliminating the need for installing
+environmental guidance such as RFID \citep{7225673} or magnetic rails
+\citep{5354591}. For inspection and surveillance purposes, the camera
+data can be streamed and recorded via the HMI. For cleaning service, the
+ASV perform its task during its movement. This necessitates that the
+path planning follows certain objects, such as road pavement or curb.
+Combined with the method proposed in \citep{SongZW_IV_2015}, the ASV can
+navigate to track arbitrary distinguishable object boundaries to conduct
+the cleaning. Nevertheless, thanks to the developed localization,
+arbitrary path rerouting is also possible. For services that require
+following certain moving object such as pedestrian \citep{7139259}, the
+LIDAR and camera sensors could be used to track the object.
+Subsequently, the tracked object positions will become the destination
+points for the ASV path planner.
+
 \section{Conclusion}\label{conclusion}
 
-That's all folks!
+The ASV has been developed to handle human service tasks. It has generic
+architecture which is reproducible for other purpose of use. During the
+development of the ASV, issues had surfaced, and dealt with current
+approaches. The main function of the ASV is to navigate through set of
+prior taught waypoints. Precise localization is achieved by combining
+GPS reading and a prior map generated using LIDAR. This allows
+adaptation to various human oriented service tasks, with appropriate
+tooling mounted. The experimental prototype results verified that the
+ASV is able to execute the path reliably and safely. Currently, the low
+level controller has been implemented in an embedded microcontroller
+platform. It is of current ongoing work that other functional modules
+will be implemented in a compact, low cost and low power compute device,
+enabling possibilities of efficiently retrofitting compact vehicles or
+existing service machines into ASVs. This full embedded implementation
+and more experiments on study to deal with specific services will be
+conducted and reported in the future.
 
@@
 
-Thanks the AV team in I2R that can accomplish many wonderful demos
-within very short period of time. This leads to the conception of this
-paper and many outstanding results that have been used in the demos.
+Thanks the Autonomous Vehicle Department in Institute for Infocomm
+Research for the accomplishment of successful demonstrations within a
+short development time. The conception of human service applications
+stemmed from this endeavor has lead to the publication of this paper.
+The project was supported by the Exploit Technologies Private Limited
+(ETPL) of the Agency for Science, Technology and Research (A*STAR) of
+Singapore.
+
+\small
 

### 2017-05-19 ieee-pandoc-template/make_paper_tex_tencon2017.sh
compiling successful after edited by Albertus

@@ -1,0 +1,11 @@
+#!/usr/bin/zsh
+pandoc \
+	--standalone \
+	--natbib \
+	--smart \
+	--listings \
+	--template=./template_conf_multian_iros2016.latex \
+	-H custom.latex \
+	--from=markdown \
+	metadata_iros2016.yaml ../IROSPaper-TENCON.md ./sections/other.md -o paper_tencon2017.tex
+

### 2017-05-20 ieee-pandoc-template/paper.tex
mend

@@
 the growth of service robotics industry in the recent years
-\citep{SVR_Nov_15}. \citeauthor{7225673} \citep{7225673} introduced
+\citep{SVR_Nov_15}. \citeauthor{7225673} {[}@7225673{]} introduced
 mobile service robot for electrical power plant inspection. This in turn
 could reduce or replace human involvement in manual inspection process.
-\citeauthor{6629559} \citep{6629559} presented an autonomous driving car
+\citeauthor{6629559} {[}@6629559{]} presented an autonomous driving car
 for research purposes that includes features that allows for urban road
-navigation. Similarly, \citeauthor{7225765} \citep{7225765} introduced a
+navigation. Similarly, \citeauthor{7225765} {[}@7225765{]} introduced a
 more advanced autonomous driving platform consisting of high performance
@@
 safety \citep{stanton1996fly}. Various effort to assist drivers has lead
-to development of ADAS system \citep{6232125, 7225760}. A DBW enables
+to development of ADAS system {[}@6232125;@7225760{]}. A DBW enables
 computerized control of the vehicle by means of replacing human drivers
 with actuators, which are usually driven by electrical motors
-\citep{1035218}. The ASV presented in this paper is retrofitted from a
+{[}@1035218{]}. The ASV presented in this paper is retrofitted from a
 compact electric vehicle \citep{SongZW_IV_2015}, and thus we studied the
@@
 that GPS data is often contain errors that is too large for autonomous
-navigation \citep{6629559}. One approach to compensate the error is to
+navigation {[}@6629559{]}. One approach to compensate the error is to
 use local lane marker or road boundary information to adjust lateral
@@
 Filter or sequential Bayes filter that involves prediction from vehicle
-motion model and measurement update cycle \citep{6550131}. The
+motion model and measurement update cycle {[}@6550131{]}. The
 measurement update computed from GPS and the feature scan matching. This
@@
 should be considered. Thus, by using a laser range sensor model for
-detection, a set \(L\) of \(n\) points which each has a range \(r_{i}\)
-and a angle \(\alpha_{i}\), measured from laser beams
-\(L=\left\{(r_{1},\alpha_{1}),...,(r_{n},\alpha_{n})\right\}\) are
+detection, a set $L$ of $n$ points which each has a range $r_{i}$ and a
+angle $\alpha_{i}$, measured from laser beams
+$L=\left\{(r_{1},\alpha_{1}),...,(r_{n},\alpha_{n})\right\}$ are
 clustered to extract objects \citep{Juric-Kavelj2008_407}. A Gaussian
@@
 subsequent points belong to one cluster satisfies the distance threshold
-\(d(r_{i},r_{i+1}) \leq D_{0}+D_{1}min(r_{i},r_{i+1})\), where \(D_{0}\)
-is the accuracy of the range data.
-\(D_{1} = \frac{3}{2}(\alpha_{i+1}-\alpha_{i})\) is a constant that
+$d(r_{i},r_{i+1}) \leq D_{0}+D_{1}min(r_{i},r_{i+1})$, where $D_{0}$ is
+the accuracy of the range data.
+$D_{1} = \frac{3}{2}(\alpha_{i+1}-\alpha_{i})$ is a constant that
 determine maximum change allowed. Point that break the threshold will be
 the start of another cluster. Processed laser scanner is represented by
-a set of clusters \(\left\{ C_{1},...,C_{m} \right\}\). Each cluster
+a set of clusters $\left\{ C_{1},...,C_{m} \right\}$. Each cluster
 consists of tuples
-\(({}^{C}r_{i},{}^{C}\alpha_{i},{}^{C}x_{i},{}^{C}y_{i})\) where
-\({}^{C}x_{i}\), \({}^{C}y_{i}\) are the Cartesian coordinate
+$({}^{C}r_{i},{}^{C}\alpha_{i},{}^{C}x_{i},{}^{C}y_{i})$ where
+${}^{C}x_{i}$, ${}^{C}y_{i}$ are the Cartesian coordinate
 representations.
@@
 proximity of each cluster, object boundaries are found by determining if
-each cluster satisfies \(w_{min} \leq d(y_{min},y_{max}) \leq w_{max}\),
-where \(w_{max}\) and \(w_{min}\) depend on widths of object of
-interest. The detected obstacles are sent the path planner to aid in
-calculation of the navigation course. Moreover, obstacle detection
-improves false recognition removal of map objects for localization
-\citep{5164269}. The cluster points of detected objects are used to
-determine areas of where measured points should be excluded from the
-localization and mapping process.
+each cluster satisfies $w_{min} \leq d(y_{min},y_{max})  \leq w_{max}$,
+where $w_{max}$ and $w_{min}$ depend on widths of object of interest.
+The detected obstacles are sent the path planner to aid in calculation
+of the navigation course. Moreover, obstacle detection improves false
+recognition removal of map objects for localization {[}@5164269{]}. The
+cluster points of detected objects are used to determine areas of where
+measured points should be excluded from the localization and mapping
+process.
 
@@
 can be achieved by the notable path planning algorithm such
-\(A^{*}\)\citep{hart1968formal}, \(D^{*}\)\citep{stentz1994optimal},
+$A^{*}$\citep{hart1968formal}, $D^{*}$\citep{stentz1994optimal},
 Rapidly-Exploring Random Trees\citep{lavalle1998rapidly}, Probabilistic
@@
 
-Where \(GB\) is gas-brake position value, \(E\) is the velocity error,
-\(dE\) is the differential error, \(k_p\) is the proportional gain,
-\(k_i\) is the integral gain, \(k_d\) is the differential gain.
+Where $GB$ is gas-brake position value, $E$ is the velocity error, $dE$
+is the differential error, $k_p$ is the proportional gain, $k_i$ is the
+integral gain, $k_d$ is the differential gain.
 
@@
 planning. The controller is based on non-linear cross track error
-\(C_{e}\) and heading error \(\theta_{e}\). Cross track error is the
-lateral distance between front axle center point \((P_{x}, P_{y})\) and
-closest reference point \((R_{x}, R_{y})\) for which exponential can be
-shown \citep{ventures2006stanley}. This term helps the vehicle to steer
-towards the path to yield \(C_{e}\) as zero when its following the path.
-The heading error \(\theta_{e}\) is calculated by difference in vehicle
-heading \(\theta\) and reference heading \(\theta_{r}\) of path at
-\((R_{x}, R_{y})\). This error term directly applies to steering angle
-\(\delta\) with some steering angle limitation.
+$C_{e}$ and heading error $\theta_{e}$. Cross track error is the lateral
+distance between front axle center point $(P_{x}, P_{y})$ and closest
+reference point $(R_{x}, R_{y})$ for which exponential can be shown
+\citep{ventures2006stanley}. This term helps the vehicle to steer
+towards the path to yield $C_{e}$ as zero when its following the path.
+The heading error $\theta_{e}$ is calculated by difference in vehicle
+heading $\theta$ and reference heading $\theta_{r}$ of path at
+$(R_{x}, R_{y})$. This error term directly applies to steering angle
+$\delta$ with some steering angle limitation.
 
@@
 
-When the cross track error \(C_{e}\) is non-zero, it adjusts \(\delta\)
-such that the intended trajectory intersects the reference path tangent
-from \((R_{x}, R_{y})\) at velocity in time \(V_{t}\) units from the
-front axle center point \((P_{x}, P_{y})\). The resulting steering
-control law by combining the two terms are shown in
-(\ref{eqn_stanley_equation}). \(k_{h}\) and \(k_{c}\) are the gain
-constants for heading error and cross error, respectively. Fig.
-\ref{fig_stanley} illustrates the geometric relationship of control
-parameters.
+When the cross track error $C_{e}$ is non-zero, it adjusts $\delta$ such
+that the intended trajectory intersects the reference path tangent from
+$(R_{x}, R_{y})$ at velocity in time $V_{t}$ units from the front axle
+center point $(P_{x}, P_{y})$. The resulting steering control law by
+combining the two terms are shown in (\ref{eqn_stanley_equation}).
+$k_{h}$ and $k_{c}$ are the gain constants for heading error and cross
+error, respectively. Fig. \ref{fig_stanley} illustrates the geometric
+relationship of control parameters.
 
@@
 multiple stack of microcontroller and relay boards in order to ensure
-safe interfacing to/from the vehicle. Fans are installed to provide
-regulate temperature inside the box.
+safe interfacing to/from the vehicle. Fans are installed to regulate
+temperature inside the box.
 
@@
 module to fuse odometry data with GPS data and the developed map based
-localization. The odometry position is derived from the equation
-\ref{eqn_simple_odometry}. The following two motion sensors are
+localization. The odometry position is derived from the
+(\ref{eqn_simple_odometry}). The following two motion sensors are
 installed in the ASV: a wheel motion sensor (Kistler Wheel Pulse
@@
 
-where \(\Delta\theta\) is the yaw rate obtained from IMU, \(\theta\) is
-the heading, \(\Delta v\) is distance obtained from wheel motion sensor,
-\(x\) and \(y\) are the Cartesian coordinates of the odometry position,
-and \(t\) is the time index which is increased every sampling time.
+where $\Delta\theta$ is the yaw rate obtained from IMU, $\theta$ is the
+heading, $\Delta v$ is distance obtained from wheel motion sensor, $x$
+and $y$ are the Cartesian coordinates of the odometry position, and $t$
+is the time index which is increased every sampling time.
 
@@
 object by emitting laser towards it and analysing its reflection.
-Compared to stereo vision systems \citep{6856563}, LIDARs generally has
+Compared to stereo vision systems {[}@6856563{]}, LIDARs generally has
 more field of view, longer detection range, and more accurate depth
@@
 surrounding object and environment shape in 25m radius is used mainly
-for localization. This LIDAR is mounted roughly \(30^{\circ}\) towards
+for localization. This LIDAR is mounted roughly $30^{\circ}$ towards
 ground purposely for detecting main features of the environment such as
@@
 information from map and GPS, thus eliminating the need for installing
-environmental guidance such as RFID \citep{7225673} or magnetic rails
-\citep{5354591}. For inspection and surveillance purposes, the camera
+environmental guidance such as RFID {[}@7225673{]} or magnetic rails
+{[}@5354591{]}. For inspection and surveillance purposes, the camera
 data can be streamed and recorded via the HMI. For cleaning service, the
@@
 arbitrary path rerouting is also possible. For services that require
-following certain moving object such as pedestrian \citep{7139259}, the
+following certain moving object such as pedestrian {[}@7139259{]}, the
 LIDAR and camera sensors could be used to track the object.
@@
 
-\section*{Acknowledgments}\label{acknowledgments}
-\addcontentsline{toc}{section}{Acknowledgments}
-
-Thanks the Autonomous Vehicle Department in Institute for Infocomm
-Research for the accomplishment of successful demonstrations within a
-short development time. The conception of human service applications
-stemmed from this endeavor has lead to the publication of this paper.
-The project was supported by the Exploit Technologies Private Limited
-(ETPL) of the Agency for Science, Technology and Research (A*STAR) of
-Singapore.
-
 \small

### 2017-09-22 ieee-pandoc-template/paper_tencon2017.tex
added paper_tencon2017.tex , and is for final

\newcommand{\CLASSINPUTtoptextmargin}{104pt}
\newcommand{\CLASSINPUTbottomtextmargin}{54pt}
\newcommand{\CLASSINPUToutersidemargin}{37pt}
\newcommand{\CLASSINPUTinnersidemargin}{54pt}

%\renewcommand{\IEEEtitletopspaceextra}{18pt}
%\documentclass[10 pt,a4paper,conference]{IEEEtran}
%\documentclass[10 pt,a4paper,conference]{IEEEconf}
\documentclass[10 pt,a4paper,conference]{IEEEtran}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript

\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}

\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Human Tracking and Following in Dynamic Environment for Service Robots},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[numbers,square]{natbib}
\bibliographystyle{IEEEtranN}

\usepackage{listings}

\usepackage{algorithm}
\usepackage{algorithmic}
%\usepackage{algpseudocode}
%\usepackage[]{algorithm2e}
\usepackage{pifont}

%\makeatletter
%\algrenewcommand\ALG@beginalgorithmic{\footnotesize}
%\makeatother

\usepackage{tabularx}
\usepackage{array}

\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\graphicspath{ {./figures/iros2016/} }

%\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

%\renewcommand{\IEEEtitletopspaceextra}{18pt}
%\title{Human Tracking and Following in Dynamic Environment for Service Robots}
\title{\LARGE \bf Human Tracking and Following in Dynamic Environment for Service Robots}

\ifCLASSOPTIONcompsoc
\usepackage[caption=false,font=normalsize,labelfon
t=sf,textfont=sf]{subfig}
\else
\usepackage[caption=false,font=footnotesize]{subfi
g}
\fi

\author{
	\IEEEauthorblockN{
		Adiwahono, A. H.\IEEEauthorrefmark{1}, 
		Saputra, V. B.\IEEEauthorrefmark{2}, 
		Ng, K. P.\IEEEauthorrefmark{5}, 
		Ren, Q.\IEEEauthorrefmark{6}, 
		Tan, B. H.\IEEEauthorrefmark{4}, 
		Chang, T.W.\IEEEauthorrefmark{3} 
		}
	\IEEEauthorblockA{%
		Institute for Infocomm Research \\
		1 Fusionopolis Way, Singapore 138632 \\
		Email: (\IEEEauthorrefmark{1}adiwahonoah  \IEEEauthorrefmark{2}saputravb  \IEEEauthorrefmark{5}ngkp  \IEEEauthorrefmark{6}renqy  \IEEEauthorrefmark{4}tanbh  \IEEEauthorrefmark{3}changtw  ) @i2r.a-star.edu.sg
	}
}

\date{}

\usepackage{color}

\definecolor{lightred}{RGB}{175,50,50}
\definecolor{lightgreen}{RGB}{0,150,0}
\definecolor{lightblue}{RGB}{50,50,175}

\lstdefinelanguage{diff}{
  morecomment=[f][\color{lightblue}]{diff },
  morecomment=[f][\color{lightblue}]{index },
  morecomment=[f][\color{lightblue}]{@@},     % group identifier
  morecomment=[f][\color{lightred}]-,         % deleted lines
  morecomment=[f][\color{lightgreen}]+,       % added lines
  morecomment=[f][\color{lightblue}]{---}, % Diff header lines (must appear after +,-)
  morecomment=[f][\color{lightblue}]{+++},
}
\hyphenation{}

\newcommand{\attn}[1]{{\color{red}#1}}
\newcommand{\desc}[1]{{\emph{\color{blue}#1}}}
\newcommand{\needcite}{\attn{\tiny{[cite]}}}
\newcommand{\todo}[1]{\colorbox{yellow}{\bf TODO: #1}}

\lstset{ %
  basicstyle=\ttfamily\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  columns=fixed,
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=10pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny, % the style that is used for the line-numbers
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  tabsize=2,                       % sets default tabsize to 2 spaces
}

\urlstyle{rm}

% Redefines (sub)paragraphs to behave more like sections
%\ifx\paragraph\undefined\else
%\let\oldparagraph\paragraph
%\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
%\fi
%\ifx\subparagraph\undefined\else
%\let\oldsubparagraph\subparagraph
%\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
%\fi

\begin{document}
\maketitle

\begin{abstract}
Robot human interactions have significant applications in dealing with
day-to-day robot service. This paper presents a novel approach for human
detection, tracking and following. A flexible and robust detection
method using a 2D laser scanner is proposed firstly. The detection
method can be adapted to various leg characteristics. The detection
result is then fed to a Kalman Filter based tracking algorithm. Owing to
the inherent ability of the embedded Kalman Filter, the tracking
algorithm is able to track specific persons and their motion. Then, a
controller is designed to follow target persons while avoiding
obstacles. Finally, a service robot, namely ISERA, is adopted in the
experiments for verifying the proposed approach. The experimental
results show the robot can following a target person both indoor and
outdoor dynamic environment.
\end{abstract}

%%\begin{IEEEkeywords}
%    %feature extraction;
%    %mobile robots;
%    %trajectory control;
%    %laser scanner;
%    %Path planning%\end{IEEEkeywords}
%

\section{Introduction}\label{introduction}

Mobile service robots, such as robotic butlers, robotic waiters, and
robotic pets, are designed to assist people in their daily lives. In
these robots, the capability to autonomously detect, track and follow a
person has been regarded as an important functionality of the robotic
systems. However, until now, it still remains a challenge that endowing
this capability to these robots when they operate in human environment.

The approaches of autonomous person following without the person having
to wear any active beacon can be classified into two categories: vision
based and laser based. Due to the low cost, RGB-D cameras are widely
adopted in the vision based approaches as the work presented in
\citep{ref0, ref1}. However, the minimum distance requirement and the
narrow field view of the RGB-D sensors limit the applications for
following persons.

The laser based approaches have an advantage in terms of large field of
view and robustness on any lighting condition. In \cite{ref3} the map
information is used to help tracking both moving and stationary person.
However, the usage of this approach will be limited on environments that
have been mapped. On the other hand, leg identification has been used
for people tracking in an unknown area (e.g.~in \cite{ref4} -
\cite{ref7}). More recently, \cite{ref7} introduces a framework for
outdoor person tracking and following for a smart wheel chair robot by
extending a trained legs detector from \cite{ref8}. In
\citep{ref9, ref10}, robotic behaviors in relation to the speed and
distance to the person being followed have been analyzed. However, the
correlation from detecting legs into tracking a person, and the
robustness when multiple people is around the person being followed has
not been explored in these studies.

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{ISERA.pdf}
\caption{(a) ISERA robot in action of tracking and following a
target person (b) The sensor and interface of ISERA service
robot}\label{fig_isera}
\end{figure}

In this paper, we propose an approach to autonomously classify, track
and follow persons in a dynamic environment for a service robot, namely
ISERA (shown in Fig. \ref{fig_isera}). Using 2D Lidar and Odometry, our
approach does not require prior map information, and benefit from wide
field of view and consistent in any lighting condition. In our approach,
a constraint based leg detection method is developed to regulate the
strictness of the leg identifier as needed. Compared to previous works
that solely track the legs, our proposed approach associate the data to
form and track a virtual target person. In this way, brief false
detections of a leg in crowded environment would not immediately made
the person jump to another location, due to physical constraints in
relation to the other leg. Two layers of Kalman filter is used to ensure
the robustness of the person tracking despite close proximity to another
person and temporary line of sight loss to the leg clusters occurred.

Another notable merit of the proposed approach is that a real time
obstacle avoidance algorithm is embedded into the feed-back motion
controller of the robot. Hence, experiments show ISERA can follow a
target person while avoid obstacles autonomously in a cluttered
environment.

The paper is organized as follows. Section II describes the mobile robot
system. The people detection, tracking and following approach is
detailed in Section III. The experiment and results are described in
Section VI. Finally, a conclusion is given in Section V.

\section{System Description}\label{system-description}

The ISERA robot is designed as a human friendly service robot that could
serve as a butler or courier in public area. ISERA is built on the top
of a differential drive mobile platform with a maximum speed of
\(1m/s\). A PC is installed inside the robot for processing and a Hokuyo
UTM-30-LX lidar is mounted about \(30cm\) from the ground, which
corresponds to sensor reading of legs below the knee, around the shank
area of average adults. The lidar provide 2D laser scan, which is used to find groups of points that fits the criterions of clusters in the environment.

\section{Person Following}\label{person-following}

\subsection{Leg Identification and Segmentation}\label{leg-identification}

%\subsubsection{Leg Segmentation}\label{leg-segmentation}

%\paragraph{Modeling and Evaluation of
%clusters}\label{modeling-and-evaluation-of-clusters}

A leg identification that build based on the principle of circle
geometric fitting is proposed. To be classified as an arc or convex shape of a leg, the middle point of
a cluster must be within a reasonable distance ratio (typically between
0.1-0.7) from the length between the cluster edges. The clusters that
pass this filter will be processed further, otherwise it will be
discarded. This filtering quickly discards any non-convex shape cluster
with minimum computation cost.

Next, the center point of the cluster is approximated as the virtual
point in the middle of the cluster leftmost and rightmost edges. For
each cluster, the distance between the lidar and the center point of
that cluster is denoted as \(z\) and will be used as a variable in the
analysis. Another addition is the algorithm could also identify a joint dual leg, where the two legs of a person standing could be very close to each other and seen as one large cluster by the sensor. When a cluster has a local minimum that is farther then the center point of the cluster, it will be dissected at the minimum point into two parts. The part with more
sampling points will be considered as a new single leg cluster and will be processed further.

%Next, the center point of the cluster is approximated as the virtual point in the middle of the cluster leftmost and rightmost edges. For each cluster, the distance between the lidar and the center point of that cluster is denoted as $z$ and will be used as a variable in the analysis. This is to facilitate the effect of distance into the perception data.

%Another addition
%is the algorithm could also identify a joint dual leg, where the two
%legs of a person standing could be very close to each other and seen as
%one large cluster by the sensor.

To analyze the single leg clusters, three criterions are used as
benchmark. First, the mean error of the inscribe angle variant (IAV) of
the cluster \citep{DBLP:conf/icra/XavierPCRN05}. The second is the error
of the standard deviation of the cluster. The third is related to the
error in the size of the cluster.
The benchmark criterion is taken from numerous measurement of an adult
humanoid model with typical cylindrical legs at varying distance \(z\)
to the lidar. The data set collected are then interpolated into a
function of distance \(z\) and kept as a benchmark values.

Instead of giving a crisp output, our
algorithm calculates the confidence of a segmented cluster to be
considered as a leg. Based on the normalized errors between the desired benchmark and
the actual measurement, an equation to formulate the confidence of a
cluster to be considered as a leg is derived as,

\begin{equation}
Leg_{c}=max(1-K_II_N-K_SS_N-K_PP_N,0)\,. \label{eq:cost}
\end{equation}

with

\begin{align*}
I_N=(|I_c-I_d(z)|)/{I_d(z)}\, \\
S_N=(|S_c-S_d(z)|)/{S_d(z)}\, \\
P_N=(|P_c-P_d(z)|)/{P_d(z)}\, \\
\end{align*}

Where \(Leg_{c}\), which has a value between \(0\) and \(1\), is the
confidence of cluster \(c\) to be considered a leg. \(I_c\), \(S_c\),
and \(P_c\) are IAV mean, IAV standard deviation, and number of points
that are calculated from sensor data, respectively. \(I_d(z)\),
\(S_d(z)\),and \(P_d(z)\) are the desired values of the IAV mean, IAV
standard deviation, and number of points in the cluster for distance
\(z\), respectively. \(K_I\), \(K_S\), and \(K_P\) are weighting factor
rule that tuned based on the preferred strictness of the leg
segmentation.

Strict leg segmentation gives the least number of false positives, and
could be used when the lidar identifies mostly bare legs. On the other
hand, if the circumstance allows us to tolerate more false positives in
the leg detection, loose segmentation could be used to detect people
that are wearing loose pants. This strictness option would provide
situational advantage compared to a rigid data trained learning based
methods in other works. Finally, for clusters that have a confidence that exceed a cut off
threshold, the center point and the confidence value are passed on to
the leg and person tracking algorithm.

\subsection{Leg and People Tracking}\label{leg-and-people-tracking}

In order to follow certain person, multiple target tracking is developed
to estimate positions of both detected legs and people. The estimation
is implemented using Kalman Filters (KFs) \citep{KalmanRudolfEmil} with
two different motion model for legs and for people. In general, the
state estimation of the legs and people can be modeled by a linear
system,
\(\boldsymbol{\mathrm{x}}_{k+1}=\boldsymbol{A} \boldsymbol{\mathrm{x}}_k + \boldsymbol{\mathrm{w}}_k\).
The process noise, \(\boldsymbol{\mathrm{w}}_k\) is modelled as Gaussian
white noise with covariance matrix \(\boldsymbol{Q}\). Fig.
\ref{fig_process_diagram} shows the flow of the people following
procedure. The input for the legs tracking are the leg detection results
in each frame \(k\). Furthermore, the input for the people tracking is
the leg tracking states, treated as observations. In contrast with our
approach, temporary people tracking are created in each update step in
\citep{ref7}. This approach could infer people directly from leg
identification, but the movements of the people are not included in the
consideration of the filter. In our method, the KF in the people
tracking maintains the state of the tracked people at all times.
Finally, the result of the people tracking is transmitted to the pursuit
controller (Sec. \ref{pursuit-controller}), so that the robot can follow
the person.

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{process_diagram.pdf}
\caption{Tracking process.}
\label{fig_process_diagram}
\end{figure}

\subsubsection{Legs Tracking}\label{legs-tracking}

The KF for the legs uses a constant velocity motion model with a pseudo
velocity measurement during the KF update steps. At discrete time \(k\),
the KF maintains a set of leg tracks,
\({}^L\boldsymbol{X}_k=\lbrace {}^L\boldsymbol{\mathrm{x}}^1_k, {}^L\boldsymbol{\mathrm{x}}^2_k,\dotsb,{}^L\boldsymbol{\mathrm{x}}^{{}^LN_k}_k \rbrace\),
where \({}^LN_k\) is the number of leg track at time \(k\). Each leg
track has a state estimate
\({}^L\boldsymbol{\mathrm{x}}^j_k=[ x \: y \: \dot{x} \: \dot{y} ]^T\)
of a target position and velocity in a 2D Cartesian coordinate. During
the update step of the Kalman Filter, leg identification are processed
using an observation model,
\({}^L\boldsymbol{\mathrm{z}}_k={}^L\boldsymbol{H}{}^L\boldsymbol{\mathrm{x}}_k + \boldsymbol{\mathrm{v}}_k\).
The observation includes position and velocity observations with white
noise, \(\boldsymbol{\mathrm{v}}_k\) governed by a covariance matrix,
\({}^L\boldsymbol{R}\). The pseudo velocity measurement is determined
from estimation of the difference from current state (after update step)
and the previous state, normalized by the time step. The velocity
measurement is used since we found that data from the laser perception
is accurate and helps to improve legs tracking accuracy. The prediction
and update cycle of the KF for every track can be summarized by the
following equation. For clarity, the indices are omitted in this
equation.

\begin{IEEEeqnarray}{c}
$$
\boldsymbol{\tilde{\mathrm{x}}}=\boldsymbol{A}\boldsymbol{\hat{\mathrm{x}}}\IEEEyesnumber\IEEEyessubnumber*\\
\boldsymbol{\tilde{P}}=\boldsymbol{A\hat{P}A}^T + \boldsymbol{Q}\\
\boldsymbol{K}=\boldsymbol{\tilde{P}H}^T(\boldsymbol{H\tilde{P}H}+ \boldsymbol{R})^{-1}\\
\boldsymbol{\hat{\mathrm{x}}}=\boldsymbol{\tilde{\mathrm{x}}}+\boldsymbol{K}(\boldsymbol{\mathrm{z}}-\boldsymbol{H\tilde{\mathrm{x}}})\\
\boldsymbol{\hat{P}}=(\boldsymbol{I}-\boldsymbol{KH})\boldsymbol{\tilde{P}},
$$
\end{IEEEeqnarray}

where \(\backsim\) and \(\wedge\) denote the predicted and filtered
quantities, \(\boldsymbol{P}\) is the covariance matrix,
\(\boldsymbol{H}\) is the observation matrix relating the state to the
observation, \(\boldsymbol{I}\) is the identity matrix and
\(\boldsymbol{K}\) is the Kalman gain. The update steps require
associations between predicted state and current observation, which is
solvable by employing Munkres algorithm \citep{munkresalgo}. The cost
matrix for the assignment problem is computed using the Mahalanobis
distance, so that the filter uncertainties are taken into account. This
method is also known as Global Nearest Neighbor. However, a global
gating threshold setting is employed so that association pairs that are
too far away will be dropped. The data association has three
interpretations: leg(s) that are uniquely associated with a track, the
legs that cannot be associated with any of the existing track(s), and
the track(s) that cannot be associated to any identified leg. Each track
has also confidence level which is increased exponentially (with a
constant \(\alpha\) as a parameter) if there is evidence. If there is no
evidence, the confidence will decrease and the track is removed if the
confidence is below certain threshold. The outcomes of the
interpretations are summarized in Table.
\ref{table:leg_tracking_outcome}. The \({}^Lc^j_k\) and \({}^Ld^j_k\)
are the confidence of the leg track and the identified leg confidence
associated with the leg track, with index \(j\) at time \(k\),
respectively.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Possible outcomes for leg tracking association}
\label{table:leg_tracking_outcome}
\centering
\footnotesize
\begin{tabular}{p{1.5cm}||p{6.cm}}
  \hline
    \textbf{Case} &
    \textbf{Outcome} \cr
  \hline\hline
    Assigned track with leg observation & Update the corresponding KF state. Track confidence is updated, ${}^Lc^j_k=\alpha \, {}^Lc^j_{k-1} + (1-\alpha) \, {}^Ld^j_{k}$\cr
  \hline
    Unassociated track & Skip update, but propagate the track using the KF predict step. Track confidence is degraded, ${}^Lc^j_k=\alpha \, {}^Lc^j_{k-1}$ \cr
  \hline
    Unassociated leg observation & Initiate a new track with zero velocity and zero confidence. \cr
  \hline
\end{tabular}
\end{table}

\subsubsection{People Tracking}\label{people-tracking}

In order to track people, additional KFs are also created similarly with
the formulation elaborated in the leg tracking method. The differences
lie on the motion model, observation model and how the data association
is treated. People tracking maintains a set of people tracks,
\({}^P\boldsymbol{X}_k=\lbrace {}^P\boldsymbol{\mathrm{x}}^1_k, {}^P\boldsymbol{\mathrm{x}}^2_k,\dotsb,{}^P\boldsymbol{\mathrm{x}}^{{}^PN_k}_k \rbrace\),
where \({}^PN_k\) is the number of people track at time \(k\). Each leg
track has a state estimate
\({}^P\boldsymbol{\mathrm{x}}^j_k=[ x \: y \: \dot{x} \: \dot{y} \: \ddot{x} \: \ddot{y} ]^T\)
of a target position, velocity, and acceleration in a 2D Cartesian
coordinate. The rationale behind the constant acceleration model for the
people tracking is that humans have walking pattern that accelerates and
decelerates periodically. The observation model takes the states of the
legs tracks as measurements,
\({}^P\boldsymbol{\mathrm{z}}^m_k={}^L\boldsymbol{\mathrm{x}}^m_k\),
where \(m=1 \dotsb {}^LN_k\). With this another layer of KF tracker, any
spurious leg identification can be robustly filtered out.

The people tracking observation model,
\({}^P\boldsymbol{\mathrm{z}}_k={}^P\boldsymbol{H}{}^P\boldsymbol{\mathrm{x}}+\boldsymbol{\mathrm{v}}_k\)
takes only position as measurement variable. If both legs of a person
can be detected, the position is computed as the center of the two legs,
otherwise it is coincide as the position of the only leg detected. The
people associations is solved using the Munkres algorithm, but the
observation targets are firstly categorized into three groups: the legs
that has unambiguous nearest leg, the legs that has uncertain leg pair
(because there are a few candidates nearby), and the legs that are
located far enough to other legs. These groups are subsequently referred
as the two-legs group, the ambiguous one-legs group, and the certain
one-legs group, respectively. The grouping is determined based on simple
search with a maximum distance between two-legs pair threshold
parameter. The data association is solved using similar cost matrix
method, however we found that for people tracking, real distance metric
is more robust. This is possibly caused by the fact that the
uncertainties of the KFs are not as accurate compared to the leg
tracking, because the observation are virtual measurement (the state of
the leg tracks). There are four interpretations of the people tracking
association: two-legs group that are uniquely associated with a people
track, two-legs group that are unassociated, the people track(s) that
are paired with only one in the one-legs group, the people track(s) that
are unpaired with any observation. The summary of the outcomes for these
interpretations is shown in Table. \ref{table:people_tracking_outcome}.
People tracks carry additional confidence information derived from its
observation from leg tracking data. The confidence is update in a
similar manner as in the leg tracking, with a constant parameter
\(\beta\). Two-legs group confidence is computed by averaging its legs
confidences, and a single confidence is derived when a people track is
associated with the one-legs group. If associated with the uncertain
one-legs group, people track confidence are not updated, i.e.~maintain
the same confidence value as it is deemed ambiguous. The track will be
removed if the confidence is below certain threshold. The \({}^Pc^j_k\)
and \({}^Pd^j_k\) are the confidence of the people track and the
confidence of the associated observation, with index \(j\) at time
\(k\), respectively.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Possible outcomes for people tracking association}
\label{table:people_tracking_outcome}
\centering
\footnotesize
\begin{tabular}{p{1.5cm}||p{6.cm}}
\hline
\textbf{Case} &
\textbf{Outcome} \cr
\hline\hline
Assigned people track with two-leg & Update the corresponding KF state. Track confidence is updated, ${}^Pc^j_k=\beta \, {}^Pc^j_{k-1} + (1-\beta) \, {}^Pd^j_{k}$\cr
\hline
Unassociated people track & Skip update, but propagate the track using the KF predict step. Track confidence is degraded, ${}^Pc^j_k=\beta \, {}^Pc^j_{k-1}$ \cr
\hline
Associated people track with one-leg & If the one-leg belongs to certain one-legs group, update the corresponding KF state and its confidence using the properties of the one-leg. \newline ,else if the one-leg is in the ambiguous group, the KF state is not updated, and the predict step is skipped for this track.\cr
\hline
Unassociated two-leg & Initiate a new track with zero velocity, zero acceleration and zero confidence. \cr
\hline
\end{tabular}
\end{table}

\subsection{Pursuit Controller}\label{pursuit-controller}

The pursuit controller drives ISERA towards the tracked target person
while avoiding obstacles. The driving control is based on the selection
of discrete spatial zones with the lowest cost. Fig.
\ref{fig_pursuit_controller} shows the variables used in the pursuit
controller. The coordinate of the target person is described in polar
coordinate with range \(R_P\), and angle \(\theta_{P}\) with respect to
the robot heading. To determine the angle \(\theta_{BP}\) where the
robot should go to pursuit the target, the area surrounding the robot
are first divided into \(m\) number of spatial `buckets'' zones. The
costs of each bucket are subject to evaluation, determined by factors
such as the angle of each bucket to the target and to obstacles.

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{PursuitIllustration.pdf}
\caption{Variables in the pursuit controller. (a) Illustration of the discrete spatial zone into $m$
number of buckets (9 buckets for illustration purpose). Note that
the nearest point to obstacle $C_{Bn}$ in bucket $n=\{1,...,m\}$ may
vary up depending on the environment (b) The parameters used in the
pursuit controller} \label{fig_pursuit_controller}
\end{figure}

A dynamic lookout distance is used to regulate the obstacle detection
area where the lookout distance of each buckets \(R_{OD}\), are kept to
be less than the range to target. The area is shrunk and expanded
proportional to the distance to the target \(R_P\). In this way, the
target person legs would not be regarded as an obstacle to be avoided.
The delta angle of each bucket with respect to the target
\(\delta_{Bn}\) is calculated as,

\begin{equation}
\delta_{Bn} = |\theta_{Bn}-\theta_{P}|\,. \label{eq:delta}
\end{equation}

where \(\theta_{Bn}\) is the angle of the center point in bucket \(n\),
and \(\theta_{P}\) is the target angle. Then, the individual cost of
each bucket is calculated as,

\begin{equation}
cost_{Bn}=\frac{\delta_{Bn}+1}{C_{Bn}}\,. \label{eq:cost}
\end{equation}

where \(C_{Bn}\) is the distance to the nearest obstacle inside the
buckets.

Naturally, when there is no obstacle inside the obstacle detection
range, the nearest bucket in the direction of the target would have the
lowest cost. However, to prevent the robot from going too near into an
obstacle, each bucket cost is also influenced by the cost of its
neighboring several buckets. By comparing the average cost of each
buckets, the center point of the bucket with the lowest average cost is
chosen to be the pursuit heading \(\theta_{BP}\).

The turn velocity \(\omega_P\) is chosen to be proportional to pursuit
heading angle \(\theta_{BP}\),

\begin{equation}
\omega_P=K_{\omega}\times\theta_{BP}\,. \label{eq:cost}
\end{equation}

Where \(K_{\omega}\) is a weighting constant.

The pursuit velocity \(v_P\), is made to be proportional to obstacle
clearance in the pursuit heading \(C_{BP}\), the angle of the target
person \(\theta_P\), and the angle of the pursuit heading
\(\theta_{BP}\). For example, to pursuit with the highest speed, there
should be no obstacle near the pursuit heading and the target person is
in front of the robot. For other cases, the velocity will be reduced
proportionally.

Another factor that has a significant impact on the robot behavior is
the social zones of the person \cite{ref10}. As a service robot, the
robot is expected to behave in the manner that is socially acceptable.
The closer the robot to the target person, the more gentle the motion
should be. The control laws combining these considerations are,

\begin{figure*}[!t]
\centering
\subfloat[Single target tracking]{\includegraphics[height=3.0in]{occluded-cropped.pdf}
\label{fig_static_result_one_people}}
\subfloat[Two targets tracking]{\includegraphics[height=3.0in]{occluded2.pdf}
\label{fig_static_result_two_people}}
\hfil
\subfloat{\includegraphics[width=1.2in]{legend.pdf}}
\caption{Tracking results for stationary robot.}
\label{fig_static_result}
\end{figure*}

\begin{equation}
v_P=\frac{C_{BP}}{K_o}\times\frac{\theta_m-\theta_P}{\theta_m}\times
\frac{\theta_m-\theta_{BP}}{\theta_m}\times D_P\,.
\label{eq:forwardvel}
\end{equation}

Where \(K_o\) is a weighting constant, and \(\theta_m\) is an angle
between the front and the edge of the perception zone. \(D_P\) is the
parameter that changes the aggressiveness of the pursuit based on the
social zone of the target person. In our ISERA, the typical values are,

\begin{eqnarray}
D_P =\hspace{-1mm} \left\{
\begin{array}{cc}
1 & \textrm{if } R_P>1.5m\\
0.6 & \textrm{if } 1m<R_P<1.5m\\
0.2 & \textrm{if } 0.3m<R_P<1m\\
0& \textrm{if } R_P<0.3m\\
\end{array}
\right.
\end{eqnarray}

\section{Experimentation and Results}\label{experimentation-and-results}

The people detection, tracking, and pursuit algorithm has been tested
both indoor and outdoor. The 2D Lidar has \(180\) degree towards the
front of the robot, which gives \(720\) sampling points with \(0.25\)
degree separating each point. The observation of clusters for leg
detection is limited to be within \(5\) meters. Cluster size is limited
to be within \(0.07m - 0.2m\) and consist more than 4 sampling points.
Clusters would be classified as legs if the confidence exceed a cut off
threshold of \(0.5\). For the pursuit controller, the area in front of
the robot are divided into \(72\) bucket zones.

\begin{figure*}[!t]
\centering
\includegraphics[width=6.5in]{Following.pdf}
\caption{ISERA tracks and follows person A (wearing blue shirt), while person B (wearing black shirt) is passing in between: (a) Person B is about to pass through between person A and ISERA. (b) For a few moments ISERA did not have line of sight of person A, and the tracker will start to decay. (c) ISERA regain line of sight and continued following person A} \label{fig:blocked}
\vspace*{4pt}
\end{figure*}

\subsection{People Detection and
Tracking}\label{people-detection-and-tracking}

A single target tracking tests are coordinated with a person walking
repeatedly from one start point and an end point following a line marked
on the floor, while ISERA is staionary. In a cluttered environment legs
could be occluded by other people or obstacles. This condition is
emulated by adding more people walking around while the primary target
is still following the straight path. In addition, tracking of two
targets of interest were conducted. The paths are two straight lines
located with a roughly \(65cm\) distance to each other.

The results of single and multiple target tracking are depicted in
Fig.\ref{fig_static_result_one_people} and
Fig.\ref{fig_static_result_two_people}, respectively. As can be seen,
the tracking was executed robustly even in the middle of cluttered
objects and some spurious leg measurements. It is observed that during
occlusions, target can sometime deviate from the ground truth due to
temporary uncertainties in the filter. By keeping the confidence level
in each track, we can maintain which target to be preserved for the next
filter cycle.

\subsection{People Following}\label{people-following}

A series of experiments in a outdoor public area with obstacles to
verify that ISERA can follow a person. The target person to be followed
is selected by having the target person standing in front of ISERA.
ISERA's pursuit controller maintains \(30cm\) distance from the person.
Some disturbance is emulated by having people walking around and in
between ISERA and the target. The results shows ISERA consistently
manage to track and follow the target person that walks below ISERA's
maximum speed (limited to \(1m/s\) in our hardware). When traveling
between obstacles, ISERA also able to avoid going too close to the
obstacle, and successfully follows the person.

\section{Conclusion}\label{conclusion}

In this paper, ISERA service robot algorithms to follow a target person
have been presented. The person tracker associate the leg to a person
and tracks based on the confidence level that is given by the leg
identifier. The pursuit algorithm could regulate control between
maintaining the distance to target person and to avoid obstacle. Future
works should mitigate possible fail scenarios when the person walks too
fast or being obstructed for a prolong period of time.

\small

                                    \renewcommand\refname{References}
                        \bibliography{paperIROS2016}

\end{document}

### 2017-09-26 ieee-pandoc-template/paper_tencon2017.tex
added WC for prest at TENCON, and fix pdfExpress compatibility (no links or bookmarks allowed)

@@
 \hypersetup{breaklinks=true,
-            bookmarks=true,
+            bookmarks=false,
             pdfauthor={},
             pdftitle={Human Tracking and Following in Dynamic Environment for Service Robots},
-            colorlinks=true,
+            colorlinks=false,
             citecolor=blue,
@@
 		Ng, K. P.\IEEEauthorrefmark{5}, 
+		Gao, W.\IEEEauthorrefmark{7}, 
 		Ren, Q.\IEEEauthorrefmark{6}, 
@@
 		1 Fusionopolis Way, Singapore 138632 \\
-		Email: (\IEEEauthorrefmark{1}adiwahonoah  \IEEEauthorrefmark{2}saputravb  \IEEEauthorrefmark{5}ngkp  \IEEEauthorrefmark{6}renqy  \IEEEauthorrefmark{4}tanbh  \IEEEauthorrefmark{3}changtw  ) @i2r.a-star.edu.sg
+		Email: (\IEEEauthorrefmark{1}adiwahonoah  \IEEEauthorrefmark{2}saputravb  \IEEEauthorrefmark{5}ngkp  \IEEEauthorrefmark{7}gaowc  \IEEEauthorrefmark{6}renqy  \IEEEauthorrefmark{4}tanbh  \IEEEauthorrefmark{3}changtw  ) @i2r.a-star.edu.sg
 	}
